---
title: "Testing Fisher"
author: "Charlie Whittaker"
date: "1/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(tidyverse)
library(ggpubr)
```
```{r}
make.df2 <- function(denomItem){
  a <- data.frame(c(2,degSize),c(pathSize,denomItem))
  x <- fisher.test(a, alternative="greater")
  return(-log(x$p.value,10))
}

make.df5 <- function(denomItem){
  a <- data.frame(c(5,degSize),c(pathSize,denomItem))
  x <- fisher.test(a, alternative="greater")
  return(-log(x$p.value,10))
}

make.df10 <- function(denomItem){
  a <- data.frame(c(10,degSize),c(pathSize,denomItem))
  x <- fisher.test(a, alternative="greater")
  return(-log(x$p.value,10))
}

make.df15 <- function(denomItem){
  a <- data.frame(c(15,degSize),c(pathSize,denomItem))
  x <- fisher.test(a, alternative="greater")
  return(-log(x$p.value,10))
}

make.df25 <- function(denomItem){
  a <- data.frame(c(25,degSize),c(pathSize,denomItem))
  x <- fisher.test(a, alternative="greater")
  return(-log(x$p.value,10))
}

make.df50 <- function(denomItem){
  a <- data.frame(c(50,degSize),c(pathSize,denomItem))
  x <- fisher.test(a, alternative="greater")
  return(-log(x$p.value,10))
}

make.df100 <- function(denomItem){
  a <- data.frame(c(100,degSize),c(pathSize,denomItem))
  x <- fisher.test(a, alternative="greater")
  return(-log(x$p.value,10))
}

make.df200 <- function(denomItem){
  a <- data.frame(c(200,degSize),c(pathSize,denomItem))
  x <- fisher.test(a, alternative="greater")
  return(-log(x$p.value,10))
}

```

*run the plots with -log10 pvalues*
```{r}
denom <- seq(from = 12000, to = 20000, by = 100)
degSize <- 1200
###########
pathSize <- 25

x2 <- lapply(denom, make.df2)
x2.Plot <- as.data.frame(cbind(denom,unlist(x2)))
colnames(x2.Plot) <- c("BkgrSize","pval")

x5 <- lapply(denom, make.df5)
x5.Plot <- as.data.frame(cbind(denom,unlist(x5)))
colnames(x5.Plot) <- c("BkgrSize","pval")

x10 <- lapply(denom, make.df10)
x10.Plot <- as.data.frame(cbind(denom,unlist(x10)))
colnames(x10.Plot) <- c("BkgrSize","pval")

x15 <- lapply(denom, make.df15)
x15.Plot <- as.data.frame(cbind(denom,unlist(x15)))
colnames(x15.Plot) <- c("BkgrSize","pval")

pl.25 <- ggplot() + geom_point(data=x2.Plot, aes(x=BkgrSize, y=pval), color="green") + geom_point(data=x5.Plot, aes(x=BkgrSize, y=pval), color="black") + geom_point(data=x10.Plot, aes(x=BkgrSize, y=pval), color="blue") + geom_point(data=x15.Plot, aes(x=BkgrSize, y=pval), color="red") + geom_hline(aes(yintercept=1.3, color = "red"), size=2)  + ylim(0, 25) + ggtitle("25 Gene Pathway")
###########
pathSize <- 50

x2 <- lapply(denom, make.df2)
x2.Plot <- as.data.frame(cbind(denom,unlist(x2)))
colnames(x2.Plot) <- c("BkgrSize","pval")

x5 <- lapply(denom, make.df5)
x5.Plot <- as.data.frame(cbind(denom,unlist(x5)))
colnames(x5.Plot) <- c("BkgrSize","pval")

x10 <- lapply(denom, make.df10)
x10.Plot <- as.data.frame(cbind(denom,unlist(x10)))
colnames(x10.Plot) <- c("BkgrSize","pval")

x15 <- lapply(denom, make.df15)
x15.Plot <- as.data.frame(cbind(denom,unlist(x15)))
colnames(x15.Plot) <- c("BkgrSize","pval")

pl.50 <- ggplot() + geom_point(data=x2.Plot, aes(x=BkgrSize, y=pval), color="green") + geom_point(data=x5.Plot, aes(x=BkgrSize, y=pval), color="black") + geom_point(data=x10.Plot, aes(x=BkgrSize, y=pval), color="blue") + geom_point(data=x15.Plot, aes(x=BkgrSize, y=pval), color="red") + geom_hline(aes(yintercept=1.3, color = "red"), size=2)  + ylim(0, 25) + ggtitle("50 Gene Pathway")
###########
pathSize <- 75

x2 <- lapply(denom, make.df2)
x2.Plot <- as.data.frame(cbind(denom,unlist(x2)))
colnames(x2.Plot) <- c("BkgrSize","pval")

x5 <- lapply(denom, make.df5)
x5.Plot <- as.data.frame(cbind(denom,unlist(x5)))
colnames(x5.Plot) <- c("BkgrSize","pval")

x10 <- lapply(denom, make.df10)
x10.Plot <- as.data.frame(cbind(denom,unlist(x10)))
colnames(x10.Plot) <- c("BkgrSize","pval")

x15 <- lapply(denom, make.df15)
x15.Plot <- as.data.frame(cbind(denom,unlist(x15)))
colnames(x15.Plot) <- c("BkgrSize","pval")

pl.75 <- ggplot() + geom_point(data=x2.Plot, aes(x=BkgrSize, y=pval), color="green") + geom_point(data=x5.Plot, aes(x=BkgrSize, y=pval), color="black") + geom_point(data=x10.Plot, aes(x=BkgrSize, y=pval), color="blue") + geom_point(data=x15.Plot, aes(x=BkgrSize, y=pval), color="red") + geom_hline(aes(yintercept=1.3, color = "red"), size=2)  + ylim(0, 25) + ggtitle("75 Gene Pathway")
###########
pathSize <- 100

x2 <- lapply(denom, make.df2)
x2.Plot <- as.data.frame(cbind(denom,unlist(x2)))
colnames(x2.Plot) <- c("BkgrSize","pval")

x5 <- lapply(denom, make.df5)
x5.Plot <- as.data.frame(cbind(denom,unlist(x5)))
colnames(x5.Plot) <- c("BkgrSize","pval")

x10 <- lapply(denom, make.df10)
x10.Plot <- as.data.frame(cbind(denom,unlist(x10)))
colnames(x10.Plot) <- c("BkgrSize","pval")

x15 <- lapply(denom, make.df15)
x15.Plot <- as.data.frame(cbind(denom,unlist(x15)))
colnames(x15.Plot) <- c("BkgrSize","pval")

pl.100 <- ggplot() + geom_point(data=x2.Plot, aes(x=BkgrSize, y=pval), color="green") + geom_point(data=x5.Plot, aes(x=BkgrSize, y=pval), color="black") + geom_point(data=x10.Plot, aes(x=BkgrSize, y=pval), color="blue") + geom_point(data=x15.Plot, aes(x=BkgrSize, y=pval), color="red") + geom_hline(aes(yintercept=1.3, color = "red"), size=2)  + ylim(0, 25) + ggtitle("100 Gene Pathway")
###########
pathSize <- 200

x2 <- lapply(denom, make.df2)
x2.Plot <- as.data.frame(cbind(denom,unlist(x2)))
colnames(x2.Plot) <- c("BkgrSize","pval")

x5 <- lapply(denom, make.df5)
x5.Plot <- as.data.frame(cbind(denom,unlist(x5)))
colnames(x5.Plot) <- c("BkgrSize","pval")

x10 <- lapply(denom, make.df10)
x10.Plot <- as.data.frame(cbind(denom,unlist(x10)))
colnames(x10.Plot) <- c("BkgrSize","pval")

x15 <- lapply(denom, make.df15)
x15.Plot <- as.data.frame(cbind(denom,unlist(x15)))
colnames(x15.Plot) <- c("BkgrSize","pval")

pl.200 <- ggplot() + geom_point(data=x2.Plot, aes(x=BkgrSize, y=pval), color="green") + geom_point(data=x5.Plot, aes(x=BkgrSize, y=pval), color="black") + geom_point(data=x10.Plot, aes(x=BkgrSize, y=pval), color="blue") + geom_point(data=x15.Plot, aes(x=BkgrSize, y=pval), color="red") + geom_hline(aes(yintercept=1.3, color = "red"), size=2)  + ylim(0, 25) + ggtitle("200 Gene Pathway")
###########
pathSize <- 500

x2 <- lapply(denom, make.df2)
x2.Plot <- as.data.frame(cbind(denom,unlist(x2)))
colnames(x2.Plot) <- c("BkgrSize","pval")

x5 <- lapply(denom, make.df5)
x5.Plot <- as.data.frame(cbind(denom,unlist(x5)))
colnames(x5.Plot) <- c("BkgrSize","pval")

x10 <- lapply(denom, make.df10)
x10.Plot <- as.data.frame(cbind(denom,unlist(x10)))
colnames(x10.Plot) <- c("BkgrSize","pval")

x15 <- lapply(denom, make.df15)
x15.Plot <- as.data.frame(cbind(denom,unlist(x15)))
colnames(x15.Plot) <- c("BkgrSize","pval")

pl.500 <- ggplot() + geom_point(data=x2.Plot, aes(x=BkgrSize, y=pval), color="green") + geom_point(data=x5.Plot, aes(x=BkgrSize, y=pval), color="black") + geom_point(data=x10.Plot, aes(x=BkgrSize, y=pval), color="blue") + geom_point(data=x15.Plot, aes(x=BkgrSize, y=pval), color="red") + geom_hline(aes(yintercept=1.3, color = "red"), size=2)  + ylim(0, 25) + ggtitle("500 Gene Pathway")
```

```{r,fig.width=20, fig.height=5}
ggarrange(pl.25,pl.50,pl.100,pl.200, legend = FALSE, ncol=4, nrow=1) 
```

*fisher tests of up in Rev vs HALLMARK_E2F*
```{r}
# < -1 FC
a <- data.frame(c(8,62-8),c(194,20237-194))
a
fisher.test(a, alternative="greater")

b <- data.frame(c(27,268-27),c(194,20237-194))
b
fisher.test(b, alternative="greater")

d.ex1 <- data.frame(c(3,297),c(37,29663))
d.ex1
fisher.test(d.ex1, alternative="greater")

d.ex2 <- data.frame(c(3-1,297),c(37+1,29663))
d.ex2
fisher.test(d.ex2, alternative="greater")
```

*Perform analysis of the impact of the numbers of deferentially expressed genes on fisher.test pvals*

```{r}
testDGEs.df <- function(degCount){
  a <- data.frame(c(degsInPath,degCount),c(pathSize,bkground))
  x <- fisher.test(a, alternative="greater")
  return(-log(x$p.value,10))
}

degSize <- seq(from = 50, to = 2000, by = 10)
bkground <- 17000
###########
pathSize <- 25

degsInPath <- 2

degs.2 <- lapply(degSize, testDGEs.df)
degs.2.Plot <- as.data.frame(cbind(degSize,unlist(degs.2)))
colnames(degs.2.Plot) <- c("degSize","pval")

degsInPath <- 5

degs.5 <- lapply(degSize, testDGEs.df)
degs.5.Plot <- as.data.frame(cbind(degSize,unlist(degs.5)))
colnames(degs.5.Plot) <- c("degSize","pval")

degsInPath <- 10

degs.10 <- lapply(degSize, testDGEs.df)
degs.10.Plot <- as.data.frame(cbind(degSize,unlist(degs.10)))
colnames(degs.10.Plot) <- c("degSize","pval")

degsInPath <- 15

degs.15 <- lapply(degSize, testDGEs.df)
degs.15.Plot <- as.data.frame(cbind(degSize,unlist(degs.15)))
colnames(degs.15.Plot) <- c("degSize","pval")

pl.25path <- ggplot() + geom_point(data=degs.2.Plot, aes(x=degSize, y=pval), color="green") + geom_point(data=degs.5.Plot, aes(x=degSize, y=pval), color="black") + geom_point(data=degs.10.Plot, aes(x=degSize, y=pval), color="blue") + geom_point(data=degs.15.Plot, aes(x=degSize, y=pval), color="red") + geom_hline(aes(yintercept=1.3, color = "red"), size=2) + ylim(0, 25) + ggtitle("25 Gene Pathway")

###########
pathSize <- 50

degsInPath <- 2

degs.2 <- lapply(degSize, testDGEs.df)
degs.2.Plot <- as.data.frame(cbind(degSize,unlist(degs.2)))
colnames(degs.2.Plot) <- c("degSize","pval")

degsInPath <- 5

degs.5 <- lapply(degSize, testDGEs.df)
degs.5.Plot <- as.data.frame(cbind(degSize,unlist(degs.5)))
colnames(degs.5.Plot) <- c("degSize","pval")

degsInPath <- 10

degs.10 <- lapply(degSize, testDGEs.df)
degs.10.Plot <- as.data.frame(cbind(degSize,unlist(degs.10)))
colnames(degs.10.Plot) <- c("degSize","pval")

degsInPath <- 15

degs.15 <- lapply(degSize, testDGEs.df)
degs.15.Plot <- as.data.frame(cbind(degSize,unlist(degs.15)))
colnames(degs.15.Plot) <- c("degSize","pval")

pl.50path <- ggplot() + geom_point(data=degs.2.Plot, aes(x=degSize, y=pval), color="green") + geom_point(data=degs.5.Plot, aes(x=degSize, y=pval), color="black") + geom_point(data=degs.10.Plot, aes(x=degSize, y=pval), color="blue") + geom_point(data=degs.15.Plot, aes(x=degSize, y=pval), color="red") + geom_hline(aes(yintercept=1.3, color = "red"), size=2) + ylim(0, 25) + ggtitle("50 Gene Pathway")
###########
pathSize <- 100

degsInPath <- 2

degs.2 <- lapply(degSize, testDGEs.df)
degs.2.Plot <- as.data.frame(cbind(degSize,unlist(degs.2)))
colnames(degs.2.Plot) <- c("degSize","pval")

degsInPath <- 5

degs.5 <- lapply(degSize, testDGEs.df)
degs.5.Plot <- as.data.frame(cbind(degSize,unlist(degs.5)))
colnames(degs.5.Plot) <- c("degSize","pval")

degsInPath <- 10

degs.10 <- lapply(degSize, testDGEs.df)
degs.10.Plot <- as.data.frame(cbind(degSize,unlist(degs.10)))
colnames(degs.10.Plot) <- c("degSize","pval")

degsInPath <- 15

degs.15 <- lapply(degSize, testDGEs.df)
degs.15.Plot <- as.data.frame(cbind(degSize,unlist(degs.15)))
colnames(degs.15.Plot) <- c("degSize","pval")

pl.100path <- ggplot() + geom_point(data=degs.2.Plot, aes(x=degSize, y=pval), color="green") + geom_point(data=degs.5.Plot, aes(x=degSize, y=pval), color="black") + geom_point(data=degs.10.Plot, aes(x=degSize, y=pval), color="blue") + geom_point(data=degs.15.Plot, aes(x=degSize, y=pval), color="red") + geom_hline(aes(yintercept=1.3, color = "red"), size=2) + ylim(0, 25) + ggtitle("100 Gene Pathway")
###########
pathSize <- 200

degsInPath <- 2

degs.2 <- lapply(degSize, testDGEs.df)
degs2.Plot <- as.data.frame(cbind(degSize,unlist(degs.2)))
colnames(degs.2.Plot) <- c("degSize","pval")

degsInPath <- 5

degs.5 <- lapply(degSize, testDGEs.df)
degs.5.Plot <- as.data.frame(cbind(degSize,unlist(degs.5)))
colnames(degs.5.Plot) <- c("degSize","pval")

degsInPath <- 10

degs.10 <- lapply(degSize, testDGEs.df)
degs.10.Plot <- as.data.frame(cbind(degSize,unlist(degs.10)))
colnames(degs.10.Plot) <- c("degSize","pval")

degsInPath <- 15

degs.15 <- lapply(degSize, testDGEs.df)
degs.15.Plot <- as.data.frame(cbind(degSize,unlist(degs.15)))
colnames(degs.15.Plot) <- c("degSize","pval")

pl.200path <- ggplot() + geom_point(data=degs.2.Plot, aes(x=degSize, y=pval), color="green") + geom_point(data=degs.5.Plot, aes(x=degSize, y=pval), color="black") + geom_point(data=degs.10.Plot, aes(x=degSize, y=pval), color="blue") + geom_point(data=degs.15.Plot, aes(x=degSize, y=pval), color="red") + geom_hline(aes(yintercept=1.3, color = "red"), size=2) + ylim(0, 25) + ggtitle("200 Gene Pathway")
```

```{r,fig.width=20, fig.height=5}
ggarrange(pl.25path, pl.50path, pl.100path,pl.200path, legend = FALSE, ncol=4, nrow=1) 
```

*Consider an experiment with large numbers differentially expressed genes and the impact of this on fisher.test pvals*

```{r, fig.width=6, fig.height=6}
testDGEs.df <- function(degCount){
  a <- data.frame(c(degsInPath,degCount),c(pathSize,20000-degCount))
  x <- fisher.test(a, alternative="greater")
  return(-log(x$p.value,10))
}

degSize <- seq(from = 1000, to = 6000, by = 10)

###########
pathSize <- 100

degsInPath <- 20

degs.20 <- lapply(degSize, testDGEs.df)
degs.20.Plot <- as.data.frame(cbind(degSize,unlist(degs.20)))
colnames(degs.20.Plot) <- c("degSize","pval")

degsInPath <- 40

degs.40 <- lapply(degSize, testDGEs.df)
degs.40.Plot <- as.data.frame(cbind(degSize,unlist(degs.40)))
colnames(degs.40.Plot) <- c("degSize","pval")

degsInPath <- 60

degs.60 <- lapply(degSize, testDGEs.df)
degs.60.Plot <- as.data.frame(cbind(degSize,unlist(degs.60)))
colnames(degs.60.Plot) <- c("degSize","pval")

degsInPath <- 80

degs.80 <- lapply(degSize, testDGEs.df)
degs.80.Plot <- as.data.frame(cbind(degSize,unlist(degs.80)))
colnames(degs.80.Plot) <- c("degSize","pval")

pl.100 <- ggplot() + geom_point(data=degs.20.Plot, aes(x=degSize, y=pval), color="green") + geom_point(data=degs.40.Plot, aes(x=degSize, y=pval), color="black") + geom_point(data=degs.60.Plot, aes(x=degSize, y=pval), color="blue") + geom_point(data=degs.80.Plot, aes(x=degSize, y=pval), color="red") + ylab(label = '-log10 pvalue') + xlab(label = 'DEG Count') + ggtitle("100 Gene Pathway")

#geom_hline(aes(yintercept=1.3, color = "red"), size=2) 

h <- 1.3
pl.100 + scale_x_continuous(limits = c(1000, 6000),breaks = c(1000, 2000, 3000, 4000, 5000, 6000)) + scale_y_continuous(limits = c(0, 15),breaks = c(0, 5, 10, 15)) + geom_hline(aes(yintercept=h, color = "red"), size=2, show.legend=FALSE) + geom_text(aes(0,h,label = h, vjust = -0.5))
```
*Consider an experiment with large numbers differentially expressed genes and the impact of this on fisher.test pvals in a larger pathway*

```{r, fig.width=6, fig.height=6}
testDGEs.df <- function(degCount){
  a <- data.frame(c(degsInPath,degCount),c(pathSize,20000-degCount))
  x <- fisher.test(a, alternative="greater")
  return(-log(x$p.value,10))
}

degSize <- seq(from = 1000, to = 6000, by = 10)
###########
pathSize <- 1000

degsInPath <- 200

degs.200 <- lapply(degSize, testDGEs.df)
degs.200.Plot <- as.data.frame(cbind(degSize,unlist(degs.200)))
colnames(degs.200.Plot) <- c("degSize","pval")

degsInPath <- 400

degs.400 <- lapply(degSize, testDGEs.df)
degs.400.Plot <- as.data.frame(cbind(degSize,unlist(degs.400)))
colnames(degs.400.Plot) <- c("degSize","pval")

degsInPath <- 600

degs.600 <- lapply(degSize, testDGEs.df)
degs.600.Plot <- as.data.frame(cbind(degSize,unlist(degs.600)))
colnames(degs.600.Plot) <- c("degSize","pval")

degsInPath <- 800

degs.800 <- lapply(degSize, testDGEs.df)
degs.800.Plot <- as.data.frame(cbind(degSize,unlist(degs.800)))
colnames(degs.800.Plot) <- c("degSize","pval")

pl.1000 <- ggplot() + geom_point(data=degs.200.Plot, aes(x=degSize, y=pval), color="green") + geom_point(data=degs.400.Plot, aes(x=degSize, y=pval), color="black") + geom_point(data=degs.600.Plot, aes(x=degSize, y=pval), color="blue") + geom_point(data=degs.800.Plot, aes(x=degSize, y=pval), color="red") + ylab(label = '-log10 pvalue') + xlab(label = 'DEG Count') + ggtitle("1000 Gene Pathway")

#geom_hline(aes(yintercept=1.3, color = "red"), size=2) 

h <- 1.3
pl.1000 + scale_x_continuous(limits = c(1000, 6000),breaks = c(1000, 2000, 3000, 4000, 5000, 6000)) + scale_y_continuous(limits = c(0, 15),breaks = c(0, 5, 10, 15)) + geom_hline(aes(yintercept=h, color = "red"), size=2, show.legend=FALSE) + geom_text(aes(0,h,label = h, vjust = -0.5))
```