---
title: "Plotting Tests - ABRF GBIRG"
author: "Charlie Whittaker"
date: "12/16/2020"
output: 
  html_document: default
  html_notebook: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*Load libraries*

```{r, warning=FALSE,error=FALSE,message=FALSE}
library(openxlsx)
library(ggplot2)
library(tidyverse)
library(ggpubr)
library(pastecs)
```

*Dataset PCA plots*
```{r}
evcPCA <- read.xlsx("evc_pca.xlsx", colNames=TRUE, rowNames=TRUE)
g1revPCA <- read.xlsx("G1vRev_pca.xlsx", colNames=TRUE, rowNames=TRUE)
avcPCA <- read.xlsx("avc_pca.xlsx", colNames=TRUE, rowNames=TRUE)
svcPCA <- read.xlsx("muscle_pca.xlsx", colNames=TRUE, rowNames=TRUE)

ggplot(evcPCA,aes(x=PC1,y=PC2, col=as.factor(group)))+
  geom_point(size=3)+
  theme_classic()+ggtitle('evc PCA')

ggplot(g1revPCA,aes(x=PC1,y=PC2, col=as.factor(group)))+
  geom_point(size=3)+
  theme_classic()+ggtitle('g1vRev PCA')

ggplot(avcPCA,aes(x=PC1,y=PC2, col=as.factor(group)))+
  geom_point(size=3)+
  theme_classic()+ggtitle('avc PCA')

ggplot(svcPCA,aes(x=PC1,y=PC2, col=as.factor(group)))+
  geom_point(size=3)+
  theme_classic()+ggtitle('svc PCA')
```

*Dataset Volcano plots*

```{r}
evcDE <- read.xlsx("../shared_data/EvC_data_vol.xlsx", colNames=TRUE, rowNames=TRUE)
evcDE <- evcDE %>% mutate(threshold = ifelse(adp <= 0.05 & abs(logFC) >= 1,"de","other"))
g1revDE <- read.xlsx("../shared_data/G1vRev_data_vol.xlsx", colNames=TRUE, rowNames=TRUE)
g1revDE <- g1revDE %>% mutate(threshold = ifelse(adp <= 0.05 & abs(logFC) >= 1,"de","other"))
avcDE <- read.xlsx("../shared_data/hpm3_AvC_data_vol.xlsx", colNames=TRUE, rowNames=TRUE)
avcDE <- avcDE %>% mutate(threshold = ifelse(adp <= 0.05 & abs(logFC) >= 1,"de","other"))
svcDE <- read.xlsx("../shared_data/musc_SkeVHeart_data_vol.xlsx", colNames=TRUE, rowNames=TRUE)
svcDE <- svcDE %>% mutate(threshold = ifelse(adp <= 0.05 & abs(logFC) >= 1,"de","other"))

ggplot(evcDE) +
        geom_point(aes(x=logFC, y=-log10(adp), color=threshold)) +
        ggtitle("EvC differential expression") +
        xlab("log2 fold change") + 
        ylab("-log10 adjusted p-value") +
        scale_y_continuous(limits = c(0,50)) +
        scale_x_continuous(limits = c(-15,15)) +
        theme(legend.position = "none",
              plot.title = element_text(size = rel(1.5), hjust = 0.5),
              axis.title = element_text(size = rel(1.25)))

ggplot(g1revDE) +
        geom_point(aes(x=logFC, y=-log10(adp), color=threshold)) +
        ggtitle("G1vRev differential expression") +
        xlab("log2 fold change") + 
        ylab("-log10 adjusted p-value") +
        scale_y_continuous(limits = c(0,50)) +
        scale_x_continuous(limits = c(-15,15)) +
        theme(legend.position = "none",
              plot.title = element_text(size = rel(1.5), hjust = 0.5),
              axis.title = element_text(size = rel(1.25)))

ggplot(avcDE) +
        geom_point(aes(x=logFC, y=-log10(adp), color=threshold)) +
        ggtitle("AvC differential expression") +
        xlab("log2 fold change") + 
        ylab("-log10 adjusted p-value") +
        scale_y_continuous(limits = c(0,50)) +
        scale_x_continuous(limits = c(-15,15)) +
        theme(legend.position = "none",
              plot.title = element_text(size = rel(1.5), hjust = 0.5),
              axis.title = element_text(size = rel(1.25)))

ggplot(svcDE) +
        geom_point(aes(x=logFC, y=-log10(adp), color=threshold)) +
        ggtitle("SvC differential expression") +
        xlab("log2 fold change") + 
        ylab("-log10 adjusted p-value") +
        scale_y_continuous(limits = c(0,50)) +
        scale_x_continuous(limits = c(-15,15)) +
        theme(legend.position = "none",
              plot.title = element_text(size = rel(1.5), hjust = 0.5),
              axis.title = element_text(size = rel(1.25)))

table(evcDE$threshold)
table(g1revDE$threshold)
table(avcDE$threshold)
table(svcDE$threshold)
```

*Import GSEA Data*

```{r}
EvC.GSEA <- read.xlsx("../shared_data/EvC_GSEAv4_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
G1vRev.GSEA <- read.xlsx("../shared_data/G1vRev_GSEAv4_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
hpm3AvC.GSEA <- read.xlsx("../shared_data/hpm3_AvC_GSEAv4_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
MuscleSvC.GSEA <- read.xlsx("../shared_data/Muscle_SkeletalvsCardiac_GSEAv4_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
```

*GSEA Summary Plots_v2*

```{r, fig.width=10, fig.height=3}
p.Cutoff <- 0.05

evc.gsea.filt <- EvC.GSEA %>% filter(FDR <= p.Cutoff) %>% filter(Collection %in% c("h","c2cgp","c2cp","c5bp", "c5mf", "c5cc"))
evc.gsea.filt <- tibble::rownames_to_column(evc.gsea.filt,"Name")
evc.gsea.nohit <- evc.gsea.filt %>% filter(Hit == "Other")
evc.gsea.hit <- evc.gsea.filt %>% filter(Hit == "Hit")
ec.gsea.plot <- ggplot() + geom_jitter(data=evc.gsea.nohit, aes(x="Collection",y=FDR), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=evc.gsea.hit, aes(x="Collection",y=FDR), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("EvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

g1vrev.gsea.filt <- G1vRev.GSEA %>% filter(FDR <= p.Cutoff) %>% filter(Collection %in% c("h","c2cgp","c2cp","c5bp", "c5mf", "c5cc"))
g1vrev.gsea.filt <- tibble::rownames_to_column(g1vrev.gsea.filt,"Name")
g1rev.gsea.nohit <- g1vrev.gsea.filt %>% filter(Hit == "Other")
g1rev.gsea.hit <- g1vrev.gsea.filt %>% filter(Hit == "Hit")
g1rev.gsea.plot <- ggplot() + geom_jitter(data=g1rev.gsea.nohit, aes(x="Collection",y=FDR), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=g1rev.gsea.hit, aes(x="Collection",y=FDR), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("g1rev") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

hpm3AvC.gsea.filt <- hpm3AvC.GSEA %>% filter(FDR <= p.Cutoff) %>% filter(Collection %in% c("h","c2cgp","c2cp","c5bp", "c5mf", "c5cc"))
hpm3AvC.gsea.filt <- tibble::rownames_to_column(hpm3AvC.gsea.filt,"Name")
ac.gsea.nohit <- hpm3AvC.gsea.filt %>% filter(Hit == "Other")
ac.gsea.hit <- hpm3AvC.gsea.filt %>% filter(Hit == "Hit")
ac.gsea.plot <- ggplot() + geom_jitter(data=ac.gsea.nohit, aes(x="Collection",y=FDR), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=ac.gsea.hit, aes(x="Collection",y=FDR), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("hpm3.AvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()


MuscleSvC.gsea.filt <- MuscleSvC.GSEA %>% filter(FDR <= p.Cutoff) %>% filter(Collection %in% c("h","c2cgp","c2cp","c5bp", "c5mf", "c5cc"))
MuscleSvC.gsea.filt <- tibble::rownames_to_column(MuscleSvC.gsea.filt,"Name")
sc.gsea.nohit <- MuscleSvC.gsea.filt %>% filter(Hit == "Other")
sc.gsea.hit <- MuscleSvC.gsea.filt %>% filter(Hit == "Hit")
sc.gsea.plot <- ggplot() + geom_jitter(data=sc.gsea.nohit, aes(x="Collection",y=FDR), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=sc.gsea.hit, aes(x="Collection",y=FDR), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("MuscleSvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

ggarrange(ec.gsea.plot,g1rev.gsea.plot,ac.gsea.plot,sc.gsea.plot, legend = FALSE, ncol=4, nrow=1)
```

*Import DAVID Data*

```{r}
EvC.DAVID <- read.xlsx("../DAVID/evcDEGS.DAVID_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
G1vRev.DAVID <- read.xlsx("../DAVID/g1vRevDEGS.DAVID_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
hpm3AvC.DAVID <- read.xlsx("../DAVID/hpm3avc.DEGS.DAVID_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
MuscleSvC.DAVID <- read.xlsx("../DAVID/muscsvc.DEGS.DAVID_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
```

*DAVID Summary Plots_v2*

```{r, fig.width=10, fig.height=3}
p.Cutoff <- 0.05

evc.david.filt <- EvC.DAVID %>% filter(PValue <= p.Cutoff)
evc.david.filt  <- tibble::rownames_to_column(evc.david.filt ,"Name")
evc.david.nohit <- evc.david.filt  %>% filter(Hit == "Other")
evc.david.hit <- evc.david.filt  %>% filter(Hit == "Hit")
ec.david.plot <- ggplot() + geom_jitter(data=evc.david.nohit, aes(x="Collection",y=PValue), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=evc.david.hit, aes(x="Collection",y=PValue), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("EvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

g1vrev.david.filt  <- G1vRev.DAVID %>% filter(PValue <= p.Cutoff)
g1vrev.david.filt  <- tibble::rownames_to_column(g1vrev.david.filt ,"Name")
g1rev.david.nohit <- g1vrev.david.filt  %>% filter(Hit == "Other")
g1rev.david.hit <- g1vrev.david.filt  %>% filter(Hit == "Hit")
g1rev.david.plot <- ggplot() + geom_jitter(data=g1rev.david.nohit, aes(x="Collection",y=PValue), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=g1rev.david.hit, aes(x="Collection",y=PValue), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("g1rev") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

hpm3AvC.david.filt  <- hpm3AvC.DAVID %>% filter(PValue <= p.Cutoff)
hpm3AvC.david.filt  <- tibble::rownames_to_column(hpm3AvC.david.filt ,"Name")
ac.david.nohit <- hpm3AvC.david.filt  %>% filter(Hit == "Other")
ac.david.hit <- hpm3AvC.david.filt  %>% filter(Hit == "Hit")
ac.david.plot <- ggplot() + geom_jitter(data=ac.david.nohit, aes(x="Collection",y=PValue), color="black", alpha=0.5, size=0.6, width=0.1) + geom_jitter(data=ac.david.hit, aes(x="Collection",y=PValue), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("hpm3.AvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()


MuscleSvC.david.filt  <- MuscleSvC.DAVID %>% filter(PValue <= p.Cutoff)
MuscleSvC.david.filt  <- tibble::rownames_to_column(MuscleSvC.david.filt ,"Name")
sc.david.nohit <- MuscleSvC.david.filt  %>% filter(Hit == "Other")
sc.david.hit <- MuscleSvC.david.filt  %>% filter(Hit == "Hit")
sc.david.plot <- ggplot() + geom_jitter(data=sc.david.nohit, aes(x="Collection",y=PValue), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=sc.david.hit, aes(x="Collection",y=PValue), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("MuscleSvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

ggarrange(ec.david.plot,g1rev.david.plot,ac.david.plot,sc.david.plot, legend = FALSE, ncol=4, nrow=1)
```

*Import gProfiler Data*

```{r}
EvC.gprofiler <- read.xlsx("../g_profiler/evc.gprofiler_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
G1vRev.gprofiler <- read.xlsx("../g_profiler/g1vrev.gprofiler_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
hpm3AvC.gprofiler <- read.xlsx("../g_profiler/hpm3avc.gprofiler_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
MuscleSvC.gprofiler <- read.xlsx("../g_profiler/muscsvc.gprofiler_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
```

*Gprofiler Summary Plots_v2*

```{r, fig.width=10, fig.height=3}
p.Cutoff <- 0.05

evc.gpro.filt  <- EvC.gprofiler %>% filter(p_value <= p.Cutoff)
evc.gpro.filt <- tibble::rownames_to_column(evc.gpro.filt,"Name")
evc.gpro.nohit <- evc.gpro.filt %>% filter(Hit == "Other")
evc.gpro.hit <- evc.gpro.filt %>% filter(Hit == "Hit")
ec.gpro.plot <- ggplot() + geom_jitter(data=evc.gpro.nohit, aes(x="Collection",y=p_value), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=evc.gpro.hit, aes(x="Collection",y=p_value), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("EvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

g1vrev.gpro.filt <- G1vRev.gprofiler %>% filter(p_value <= p.Cutoff)
g1vrev.gpro.filt <- tibble::rownames_to_column(g1vrev.gpro.filt,"Name")
g1rev.gpro.nohit <- g1vrev.gpro.filt %>% filter(Hit == "Other")
g1rev.gpro.hit <- g1vrev.gpro.filt %>% filter(Hit == "Hit")
g1rev.gpro.plot <- ggplot() + geom_jitter(data=g1rev.gpro.nohit, aes(x="Collection",y=p_value), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=g1rev.gpro.hit, aes(x="Collection",y=p_value), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("g1rev") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

hpm3AvC.gpro.filt <- hpm3AvC.gprofiler %>% filter(p_value <= p.Cutoff)
hpm3AvC.gpro.filt <- tibble::rownames_to_column(hpm3AvC.gpro.filt,"Name")
ac.gpro.nohit <- hpm3AvC.gpro.filt %>% filter(Hit == "Other")
ac.gpro.hit <- hpm3AvC.gpro.filt %>% filter(Hit == "Hit")
ac.gpro.plot <- ggplot() + geom_jitter(data=ac.gpro.nohit, aes(x="Collection",y=p_value), color="black", alpha=0.5, size=0.6, width=0.1) + geom_jitter(data=ac.gpro.hit, aes(x="Collection",y=p_value), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("hpm3.AvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()


MuscleSvC.gpro.filt <- MuscleSvC.gprofiler %>% filter(p_value <= p.Cutoff)
MuscleSvC.gpro.filt <- tibble::rownames_to_column(MuscleSvC.gpro.filt,"Name")
sc.gpro.nohit <- MuscleSvC.gpro.filt %>% filter(Hit == "Other")
sc.gpro.hit <- MuscleSvC.gpro.filt %>% filter(Hit == "Hit")
sc.gpro.plot <- ggplot() + geom_jitter(data=sc.gpro.nohit, aes(x="Collection",y=p_value), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=sc.gpro.hit, aes(x="Collection",y=p_value), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("MuscleSvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

ggarrange(ec.gpro.plot,g1rev.gpro.plot,ac.gpro.plot,sc.gpro.plot, legend = FALSE, ncol=4, nrow=1)
```

*Import Metacore Data*

```{r}
EvC.metacore <- read.xlsx("../shared_data/EvC_metacore_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
G1vRev.metacore <- read.xlsx("../shared_data/G1vRev_metacore_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
hpm3AvC.metacore <- read.xlsx("../shared_data/hpm3_AvC_metacore_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
MuscleSvC.metacore <- read.xlsx("../shared_data/Muscle_SkeletalvsCardiac_metacore_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
```

*Metacore Summary Plots_v2*

```{r, fig.width=10, fig.height=3}
p.Cutoff <- 0.05

evc.mcore.filt <- EvC.metacore %>% filter(FDR <= p.Cutoff)     
evc.mcore.filt <- tibble::rownames_to_column(evc.mcore.filt,"Name")
evc.mcore.nohit <- evc.mcore.filt %>% filter(Hit == "Other")
evc.mcore.hit <- evc.mcore.filt %>% filter(Hit == "Hit")
ec.mcore.plot <- ggplot() + geom_jitter(data=evc.mcore.nohit, aes(x="Collection",y=FDR), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=evc.mcore.hit, aes(x="Collection",y=FDR), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("EvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()        

g1vrev.mcore.filt <- G1vRev.metacore %>% filter(FDR <= p.Cutoff)     
g1vrev.mcore.filt <- tibble::rownames_to_column(g1vrev.mcore.filt,"Name")
g1rev.mcore.nohit <- g1vrev.mcore.filt %>% filter(Hit == "Other")
g1rev.mcore.hit <- g1vrev.mcore.filt %>% filter(Hit == "Hit")
g1rev.mcore.plot <- ggplot() + geom_jitter(data=g1rev.mcore.nohit, aes(x="Collection",y=FDR), color="black", alpha=0.4, size=0.6, width=0.1) + theme_void() + ggtitle("g1rev") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

#no significant g1rev hits for metacore so this line was extracted
#geom_jitter(data=g1rev.mcore.hit, aes(x="Collection",y=FDR), color="red", alpha=1, size=2, width=0.1)

hpm3AvC.mcore.filt <- hpm3AvC.metacore %>% filter(FDR <= p.Cutoff)     
hpm3AvC.mcore.filt <- tibble::rownames_to_column(hpm3AvC.mcore.filt,"Name")
ac.mcore.nohit <- hpm3AvC.mcore.filt %>% filter(Hit == "Other")
ac.mcore.hit <- hpm3AvC.mcore.filt %>% filter(Hit == "Hit")
ac.mcore.plot <- ggplot() + geom_jitter(data=ac.mcore.nohit, aes(x="Collection",y=FDR), color="black", alpha=0.5, size=0.6, width=0.1) + geom_jitter(data=ac.mcore.hit, aes(x="Collection",y=FDR), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("hpm3.AvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip() 

MuscleSvC.mcore.filt <- MuscleSvC.metacore %>% filter(FDR <= p.Cutoff)     
MuscleSvC.mcore.filt <- tibble::rownames_to_column(MuscleSvC.mcore.filt,"Name")
sc.mcore.nohit <- MuscleSvC.mcore.filt %>% filter(Hit == "Other")
sc.mcore.hit <- MuscleSvC.mcore.filt %>% filter(Hit == "Hit")
sc.mcore.plot <- ggplot() + geom_jitter(data=sc.mcore.nohit, aes(x="Collection",y=FDR), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=sc.mcore.hit, aes(x="Collection",y=FDR), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("MuscleSvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

ggarrange(ec.mcore.plot,g1rev.mcore.plot,ac.mcore.plot,sc.mcore.plot, legend = FALSE, ncol=4, nrow=1)
```

*Import IPA Data*
```{r}
EvC.ipa <- read.xlsx("../shared_data/EvC_ipa_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
G1vRev.ipa <- read.xlsx("../shared_data/G1vRev_ipa_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
hpm3AvC.ipa <- read.xlsx("../shared_data/hpm3_AvC_ipa_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
MuscleSvC.ipa <- read.xlsx("../shared_data/Muscle_SkeletalvsCardiac_ipa_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
```

*IPA Summary Plots_v2*

```{r, fig.width=10, fig.height=3}
p.Cutoff <- 0.05

evc.ipa.filt <- EvC.ipa %>% filter(p_value <= p.Cutoff)          
evc.ipa.filt <- tibble::rownames_to_column(evc.ipa.filt,"Name")
evc.ipa.nohit <- evc.ipa.filt %>% filter(Hit == "Other")  
evc.ipa.hit <- evc.ipa.filt %>% filter(Hit == "Hit")  
ec.ipa.plot <- ggplot() + geom_jitter(data=evc.ipa.nohit, aes(x="Collection",y=p_value), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=evc.ipa.hit, aes(x="Collection",y=p_value), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("EvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()              

g1vrev.ipa.filt <- G1vRev.ipa %>% filter(p_value <= p.Cutoff)          
g1vrev.ipa.filt <- tibble::rownames_to_column(g1vrev.ipa.filt,"Name")
g1rev.ipa.nohit <- g1vrev.ipa.filt %>% filter(Hit == "Other")  
g1rev.ipa.hit <- g1vrev.ipa.filt %>% filter(Hit == "Hit")  
g1rev.ipa.plot <- ggplot() + geom_jitter(data=g1rev.ipa.nohit, aes(x="Collection",y=p_value), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=g1rev.ipa.hit, aes(x="Collection",y=p_value), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("g1rev") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()              

hpm3AvC.ipa.filt <- hpm3AvC.ipa %>% filter(p_value <= p.Cutoff)          
hpm3AvC.ipa.filt <- tibble::rownames_to_column(hpm3AvC.ipa.filt,"Name")
ac.ipa.nohit <- hpm3AvC.ipa.filt %>% filter(Hit == "Other")  
ac.ipa.hit <- hpm3AvC.ipa.filt %>% filter(Hit == "Hit")  
ac.ipa.plot <- ggplot() + geom_jitter(data=ac.ipa.nohit, aes(x="Collection",y=p_value), color="black", alpha=0.5, size=0.6, width=0.1) + geom_jitter(data=ac.ipa.hit, aes(x="Collection",y=p_value), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("hpm3.AvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()              


MuscleSvC.ipa.filt <- MuscleSvC.ipa %>% filter(p_value <= p.Cutoff)          
MuscleSvC.ipa.filt <- tibble::rownames_to_column(MuscleSvC.ipa.filt,"Name")
sc.ipa.nohit <- MuscleSvC.ipa.filt %>% filter(Hit == "Other")  
sc.ipa.hit <- MuscleSvC.ipa.filt %>% filter(Hit == "Hit")  
sc.ipa.plot <- ggplot() + geom_jitter(data=sc.ipa.nohit, aes(x="Collection",y=p_value), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=sc.ipa.hit, aes(x="Collection",y=p_value), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("MuscleSvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()              

ggarrange(ec.ipa.plot,g1rev.ipa.plot,ac.ipa.plot,sc.ipa.plot, legend = FALSE, ncol=4, nrow=1)        
```

*Import iPathway Data*

```{r}
EvC.ipath <- read.xlsx("../shared_data/EvC_ipathway_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
G1vRev.ipath <- read.xlsx("../shared_data/G1vRev_ipathway_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
hpm3AvC.ipath <- read.xlsx("../shared_data/hpm3_AvC_ipathway_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
MuscleSvC.ipath <- read.xlsx("../shared_data/Muscle_SkeletalvsCardiac_ipathway_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
```

*iPathway Summary Plots*

```{r, fig.width=10, fig.height=3}
p.Cutoff <- 0.05

evc.ipath.filt <- EvC.ipath %>% filter(pv_fdr <= p.Cutoff)          
evc.ipath.filt <- tibble::rownames_to_column(evc.ipath.filt,"UniqName")
evc.ipath.nohit <- evc.ipath.filt %>% filter(Hit == "Other")  
evc.ipath.hit <- evc.ipath.filt %>% filter(Hit == "Hit")  
ec.ipath.plot <- ggplot() + geom_jitter(data=evc.ipath.nohit, aes(x="Collection",y=pv_fdr), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=evc.ipath.hit, aes(x="Collection",y=pv_fdr), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("EvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()              

g1vrev.ipath.filt <- G1vRev.ipath %>% filter(pv_fdr <= p.Cutoff)          
g1vrev.ipath.filt <- tibble::rownames_to_column(g1vrev.ipath.filt,"UniqName")
g1rev.ipath.nohit <- g1vrev.ipath.filt %>% filter(Hit == "Other")  
g1rev.ipath.hit <- g1vrev.ipath.filt %>% filter(Hit == "Hit")  
g1rev.ipath.plot <- ggplot() + geom_jitter(data=g1rev.ipath.nohit, aes(x="Collection",y=pv_fdr), color="black", alpha=0.4, size=0.6, width=0.1) + theme_void() + ggtitle("g1rev") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()              

#no hits here so this line was extracted
#geom_jitter(data=g1rev.ipath.hit, aes(x="Collection",y=pv_fdr), color="red", alpha=1, size=2, width=0.1)

hpm3AvC.ipath.filt <- hpm3AvC.ipath %>% filter(pv_fdr <= p.Cutoff)          
hpm3AvC.ipath.filt <- tibble::rownames_to_column(hpm3AvC.ipath.filt,"UniqName")
ac.ipath.nohit <- hpm3AvC.ipath.filt %>% filter(Hit == "Other")  
ac.ipath.hit <- hpm3AvC.ipath.filt %>% filter(Hit == "Hit")  
ac.ipath.plot <- ggplot() + geom_jitter(data=ac.ipath.nohit, aes(x="Collection",y=pv_fdr), color="black", alpha=0.5, size=0.6, width=0.1) + geom_jitter(data=ac.ipath.hit, aes(x="Collection",y=pv_fdr), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("hpm3.AvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()              


MuscleSvC.ipath.filt <- MuscleSvC.ipath %>% filter(pv_fdr <= p.Cutoff)          
MuscleSvC.ipath.filt <- tibble::rownames_to_column(MuscleSvC.ipath.filt,"UniqName")
sc.ipath.nohit <- MuscleSvC.ipath.filt %>% filter(Hit == "Other")  
sc.ipath.hit <- MuscleSvC.ipath.filt %>% filter(Hit == "Hit")  
sc.ipath.plot <- ggplot() + geom_jitter(data=sc.ipath.nohit, aes(x="Collection",y=pv_fdr), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=sc.ipath.hit, aes(x="Collection",y=pv_fdr), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("MuscleSvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()              

ggarrange(ec.ipath.plot,g1rev.ipath.plot,ac.ipath.plot,sc.ipath.plot, legend = FALSE, ncol=4, nrow=1)        
```

*Plotting the full EvC GSEA results*

```{r, fig.width=12, fig.height=6}
EvC.gsea.select <- EvC.GSEA  %>% filter(Collection %in% c("h","c2cgp","c2cp","c5bp", "c5mf", "c5cc"))
EvC.gsea.select <- tibble::rownames_to_column(EvC.gsea.select,"Term")
EvC.gsea.select.nohit <- EvC.gsea.select %>% filter(Hit == "Other")
EvC.gsea.select.hit <- EvC.gsea.select %>% filter(Hit == "Hit")

ggplot() + geom_jitter(data=EvC.gsea.select.nohit, aes(x=Collection,y=FDR), color="black", alpha=0.3, size=0.6, width=0.1) + geom_jitter(data=EvC.gsea.select.hit, aes(x=Collection,y=FDR), color="red", alpha=1, size=2, width=0.1) + theme_bw() + coord_flip()
```

*Plotting the full G1Rev.RevDEGS gprofiler results*

```{r, fig.width=12, fig.height=6}
G1vRev.RevDEGS.gprofiler <- read.xlsx("../g_profiler/g1vrev.RevDegs.gprofilerPlusOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
alp.val <- 1
pt.size <- 2

G1vRev.RevDEGS.gprofiler.nohit <- G1vRev.RevDEGS.gprofiler %>% filter(E2F.Hit == "Other")
G1vRev.RevDEGS.gprofiler.low <- G1vRev.RevDEGS.gprofiler %>% filter(E2F.Hit == "Low")
G1vRev.RevDEGS.gprofiler.hit <- G1vRev.RevDEGS.gprofiler %>% filter(E2F.Hit == "Hit")

ggplot() + geom_jitter(data=G1vRev.RevDEGS.gprofiler.nohit, aes(x=source,y=p_value), color="black", alpha=alp.val, size=pt.size, width=0.1) + geom_jitter(data=G1vRev.RevDEGS.gprofiler.low, aes(x=source,y=p_value), color="blue", alpha=alp.val, size=pt.size, width=0.1) + geom_jitter(data=G1vRev.RevDEGS.gprofiler.hit, aes(x=source,y=p_value), color="red", alpha=alp.val, size=pt.size+1, width=0.1) + theme_bw() + coord_flip()
```

*Plotting the EvC KEGG summary to highlight PPAR results*

```{r, fig.width=12, fig.height=6}
evc.KEGG <- read.xlsx("../shared_data/EvC_KEGG_Summary.xlsx", colNames=TRUE, rowNames=TRUE)

evc.KEGG.ppar <- evc.KEGG %>% filter(Group == "PPAR")
evc.KEGG.other <- evc.KEGG %>% filter(Group == "Other")

ggplot() + geom_jitter(data=evc.KEGG.other, aes(x=Method,y=pval), color="black", alpha=0.5, size=2, width=0.1) + geom_jitter(data=evc.KEGG.ppar, aes(x=Method,y=pval), color="red", alpha=1, size=4, width=0.1) + theme_bw() + coord_flip()
```

*G1vRev - DAVID Fold Change and Direction Analyses*

```{r, fig.width=15, fig.height=6}
p.Cutoff <- 1

G1vRev.DAVID <- read.xlsx("../DAVID/g1vRev.DEGS.1.DAVID_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
G1vRev.DAVID.FC.58 <- read.xlsx("../DAVID/g1vRev.DEGS.58.DAVID_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
G1vRev.DAVID.RevDEGS <- read.xlsx("../DAVID/g1vRev.revDEGS.1.DAVID_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
G1vRev.DAVID.RevDEGS.58 <- read.xlsx("../DAVID/g1vRev.revDEGS.58.DAVID_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)

g1vrev.david.filt  <- G1vRev.DAVID %>% filter(Bonferroni <= p.Cutoff)
g1vrev.david.filt  <- tibble::rownames_to_column(g1vrev.david.filt ,"Name")
g1rev.david.nohit <- g1vrev.david.filt  %>% filter(Hit == "Other")
g1rev.david.hit <- g1vrev.david.filt  %>% filter(Hit == "Hit")
g1rev.david.plot <- ggplot() + geom_jitter(data=g1rev.david.nohit, aes(x=Category,y=Bonferroni), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=g1rev.david.hit, aes(x=Category,y=Bonferroni), color="red", alpha=1, size=2, width=0.1) + ggtitle("g1rev") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

g1vrev.david.fc.58.filt  <- G1vRev.DAVID.FC.58 %>% filter(Bonferroni <= p.Cutoff)
g1vrev.david.fc.58.filt  <- tibble::rownames_to_column(g1vrev.david.fc.58.filt ,"Name")
g1rev.david.fc.58.nohit <- g1vrev.david.fc.58.filt  %>% filter(Hit == "Other")
g1rev.david.fc.58.hit <- g1vrev.david.fc.58.filt  %>% filter(Hit == "Hit")
g1rev.david.fc.58.plot <- ggplot() + geom_jitter(data=g1rev.david.fc.58.nohit, aes(x=Category,y=Bonferroni), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=g1rev.david.fc.58.hit, aes(x=Category,y=Bonferroni), color="red", alpha=1, size=2, width=0.1)  + ggtitle("g1rev.fc.58") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

g1vrev.david.revdegs.filt  <- G1vRev.DAVID.RevDEGS %>% filter(Bonferroni <= p.Cutoff)
g1vrev.david.revdegs.filt  <- tibble::rownames_to_column(g1vrev.david.revdegs.filt ,"Name")
g1rev.david.revdegs.nohit <- g1vrev.david.revdegs.filt  %>% filter(Hit == "Other")
g1rev.david.revdegs.hit <- g1vrev.david.revdegs.filt  %>% filter(Hit == "Hit")
g1rev.david.revdegs.plot <- ggplot() + geom_jitter(data=g1rev.david.revdegs.nohit, aes(x=Category,y=Bonferroni), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=g1rev.david.revdegs.hit, aes(x=Category,y=Bonferroni), color="red", alpha=1, size=2, width=0.1) + ggtitle("g1rev.revdegs") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

g1vrev.david.revdegs.58.filt  <- G1vRev.DAVID.RevDEGS.58 %>% filter(Bonferroni <= p.Cutoff)
g1vrev.david.revdegs.58.filt  <- tibble::rownames_to_column(g1vrev.david.revdegs.58.filt ,"Name")
g1rev.david.revdegs.58.nohit <- g1vrev.david.revdegs.58.filt  %>% filter(Hit == "Other")
g1rev.david.revdegs.58.hit <- g1vrev.david.revdegs.58.filt  %>% filter(Hit == "Hit")
g1rev.david.revdegs.58.plot <- ggplot() + geom_jitter(data=g1rev.david.revdegs.58.nohit, aes(x=Category,y=Bonferroni), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=g1rev.david.revdegs.58.hit, aes(x=Category,y=Bonferroni), color="red", alpha=1, size=2, width=0.1) + ggtitle("g1rev.revdegs.58") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

ggarrange(g1rev.david.plot,g1rev.david.fc.58.plot,g1rev.david.revdegs.plot,g1rev.david.revdegs.58.plot, legend = FALSE, ncol=2, nrow=2)
```

*G1vRev - gprofiler Fold Change and Direction Analyses*

```{r, fig.width=15, fig.height=6}
p.Cutoff <- 0.1

G1vRev.gpro <- read.xlsx("../g_profiler/g1vrev.Degs.1.gprofiler_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
G1vRev.gpro.FC.58 <- read.xlsx("../g_profiler/g1vrev.Degs.58.gprofiler_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
G1vRev.gpro.RevDEGS <- read.xlsx("../g_profiler/g1vrev.revDegs.1.gprofiler_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
G1vRev.gpro.RevDEGS.58 <- read.xlsx("../g_profiler/g1vrev.revDegs.58.gprofiler_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)

g1vrev.gpro.filt  <- G1vRev.gpro %>% filter(p_value <= p.Cutoff) 
g1vrev.gpro.filt  <- tibble::rownames_to_column(g1vrev.gpro.filt ,"Name")  
g1rev.gpro.nohit <- g1vrev.gpro.filt  %>% filter(Hit == "Other")  
g1rev.gpro.hit <- g1vrev.gpro.filt  %>% filter(Hit == "Hit")  
g1rev.gpro.plot <- ggplot() + geom_jitter(data=g1rev.gpro.nohit, aes(x=source,y=p_value), color="black", alpha=0.4, size=1, width=0.2) + geom_jitter(data=g1rev.gpro.hit, aes(x=source,y=p_value), color="red", alpha=1, size=2, width=0.2) + ggtitle("g1rev") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()   

g1vrev.gpro.fc.58.filt  <- G1vRev.gpro.FC.58 %>% filter(p_value <= p.Cutoff) 
g1vrev.gpro.fc.58.filt  <- tibble::rownames_to_column(g1vrev.gpro.fc.58.filt ,"Name")  
g1rev.gpro.fc.58.nohit <- g1vrev.gpro.fc.58.filt  %>% filter(Hit == "Other")  
g1rev.gpro.fc.58.hit <- g1vrev.gpro.fc.58.filt  %>% filter(Hit == "Hit")  
g1rev.gpro.fc.58.plot <- ggplot() + geom_jitter(data=g1rev.gpro.fc.58.nohit, aes(x=source,y=p_value), color="black", alpha=0.4, size=1, width=0.2) + geom_jitter(data=g1rev.gpro.fc.58.hit, aes(x=source,y=p_value), color="red", alpha=1, size=2, width=0.2) + ggtitle("g1rev.fc.58") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()   

g1vrev.gpro.revdegs.filt  <- G1vRev.gpro.RevDEGS %>% filter(p_value <= p.Cutoff) 
g1vrev.gpro.revdegs.filt  <- tibble::rownames_to_column(g1vrev.gpro.revdegs.filt ,"Name")  
g1rev.gpro.revdegs.nohit <- g1vrev.gpro.revdegs.filt  %>% filter(Hit == "Other")  
g1rev.gpro.revdegs.hit <- g1vrev.gpro.revdegs.filt  %>% filter(Hit == "Hit")  
g1rev.gpro.revdegs.plot <- ggplot() + geom_jitter(data=g1rev.gpro.revdegs.nohit, aes(x=source,y=p_value), color="black", alpha=0.4, size=1, width=0.2) + geom_jitter(data=g1rev.gpro.revdegs.hit, aes(x=source,y=p_value), color="red", alpha=1, size=2, width=0.2) + ggtitle("g1rev.revdegs") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

g1vrev.gpro.revdegs.58.filt  <- G1vRev.gpro.RevDEGS.58 %>% filter(p_value <= p.Cutoff) 
g1vrev.gpro.revdegs.58.filt  <- tibble::rownames_to_column(g1vrev.gpro.revdegs.58.filt ,"Name")  
g1rev.gpro.revdegs.58.nohit <- g1vrev.gpro.revdegs.58.filt  %>% filter(Hit == "Other")  
g1rev.gpro.revdegs.58.hit <- g1vrev.gpro.revdegs.58.filt  %>% filter(Hit == "Hit")  
g1rev.gpro.revdegs.58.plot <- ggplot() + geom_jitter(data=g1rev.gpro.revdegs.58.nohit, aes(x=source,y=p_value), color="black", alpha=0.4, size=1, width=0.2) + geom_jitter(data=g1rev.gpro.revdegs.58.hit, aes(x=source,y=p_value), color="red", alpha=1, size=2, width=0.2) + ggtitle("g1rev.revdegs.58") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

ggarrange(g1rev.gpro.plot,g1rev.gpro.fc.58.plot,g1rev.gpro.revdegs.plot,g1rev.gpro.revdegs.58.plot, legend = FALSE, ncol=2, nrow=2)    
```

*Plotting the hpm3 AvC Pathway data to highlight IL1 results*

```{r, fig.width=12, fig.height=6}
evc.KEGG <- read.xlsx("../shared_data/EvC_KEGG_Summary.xlsx", colNames=TRUE, rowNames=TRUE)

evc.KEGG.ppar <- evc.KEGG %>% filter(Group == "PPAR")
evc.KEGG.other <- evc.KEGG %>% filter(Group == "Other")

ggplot() + geom_jitter(data=evc.KEGG.other, aes(x=Method,y=pval), color="black", alpha=0.5, size=2, width=0.1) + geom_jitter(data=evc.KEGG.ppar, aes(x=Method,y=pval), color="red", alpha=1, size=4, width=0.1) + theme_bw() + coord_flip()
```

*msigdb plots*
```{r}
msig7.2 <- read.xlsx("../shared_data/msigdb_genesetsInfo_v7.2_paperSubset.xlsx", colNames=TRUE, rowNames=TRUE)
sub300 <- msig7.2 %>% filter(Size <= 300)
plus300 <- msig7.2 %>% filter(Size > 300)
ggplot(msig7.2, aes(Group, Size)) + geom_boxplot() + coord_cartesian(ylim = c(0, 300)) + 
  scale_x_discrete(limits = c("HALLMARK", "c2cgp", "c2cp", "KEGG", "BIOCARTA", "PID", "REACTOME", "WP", "c5bp", "c5cc", "c5mf"))
table(plus300$Group)
table(sub300$Group)
table(msig7.2$Group)
as.data.frame(msig7.2 %>% group_by(Group) %>% summarize(n(),median(Size), mean(Size)))
```

*GSEA plots - these are not looking like I want them to for the paper - just use default plots*
```{r}
source("replotGSEA.R")

replotGSEA("C:/Users/Charlie/ABRF_GBIRG_OntologyStudy/dataset_gsea/dataset_runs/avc_TNF.GseaPreranked.1613569188946", 
           gene.set ="HALLMARK_TNFA_SIGNALING_VIA_NFKB", "A", metric.range = c(-50,50), enrichment.score.range = c(-1,1))

replotGSEA("C:/Users/Charlie/ABRF_GBIRG_OntologyStudy/dataset_gsea/dataset_runs/evc_KEGG_PPAR.GseaPreranked.1613569183925", 
           gene.set ="KEGG_PPAR_SIGNALING_PATHWAY", "A", metric.range = c(-50,50), enrichment.score.range = c(-1,1))

replotGSEA("C:/Users/Charlie/ABRF_GBIRG_OntologyStudy/dataset_gsea/dataset_runs/g1vrev_E2F.GseaPreranked.1613569193955", 
           gene.set ="HALLMARK_E2F_TARGETS", "A", metric.range = c(-50,50), enrichment.score.range = c(-1,1))

replotGSEA("C:/Users/Charlie/ABRF_GBIRG_OntologyStudy/dataset_gsea/dataset_runs/svc_SKEMUSC.GseaPreranked.1613569198989", 
           gene.set ="GO_SKELETAL_MUSCLE_CONTRACTION", "A", metric.range = c(-50,50), enrichment.score.range = c(-1,1))
```

*Summary Tables*

```{r}
table(EvC.gsea.select$Collection,EvC.gsea.select$Hit)
table(evc.gsea.filt$Collection,evc.gsea.filt$Hit)
#table(EvC.gsea.select.hit$Collection,EvC.gsea.select.hit$Hit)
#table(EvC.gsea.select.nohit$Collection,EvC.gsea.select.nohit$Hit)
```
## write session info*

```{r}
sessionInfo()
writeLines(capture.output(sessionInfo()), "sessionInfo.txt")
```