---
title: "Plotting Tests - ABRF GBIRG"
author: "Charlie Whittaker"
date: "12/16/2020"
output: 
  html_document: default
  html_notebook: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*Load libraries*

```{r, warning=FALSE,error=FALSE,message=FALSE}
library(openxlsx)
library(ggplot2)
library(tidyverse)
library(ggpubr)
```

*Import GSEA Data*

```{r}
EvC.GSEA <- read.xlsx("../shared_data/EvC_GSEAv4_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
G1vRev.GSEA <- read.xlsx("../shared_data/G1vRev_GSEAv4_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
hpm3AvC.GSEA <- read.xlsx("../shared_data/hpm3_AvC_GSEAv4_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
MuscleSvC.GSEA <- read.xlsx("../shared_data/Muscle_SkeletalvsCardiac_GSEAv4_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
```

*GSEA Summary Plots*

# ```{r, fig.width=10, fig.height=3}
# evc <- EvC.GSEA %>% filter(FDR <= 0.05) %>% filter(Collection %in% c("h","c2cgp","c2cp","c5bp", "c5mf", "c5cc"))
# evc <- tibble::rownames_to_column(evc,"Name")
# ec.gsea.plot <- ggplot() + geom_jitter(data=evc, aes(x="Group",y=FDR, color=factor(Hit), alpha=Hit, size=Hit), width=0.1) + scale_alpha_manual(values=c(1, 0.05)) + scale_size_manual(values=c(3, 1)) + scale_color_manual(values=c("red","black"))+ coord_flip() + theme_void() + ggtitle("EvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1))
# 
# g1vrev <- G1vRev.GSEA %>% filter(FDR <= 0.05) %>% filter(Collection %in% c("h","c2cgp","c2cp","c5bp", "c5mf", "c5cc"))
# g1vrev <- tibble::rownames_to_column(g1vrev,"Name")
# g1rev.gsea.plot <- ggplot() + geom_jitter(data=g1vrev, aes(x="Group",y=FDR, color=factor(Hit), alpha=Hit, size=Hit), width=0.1) + scale_alpha_manual(values=c(1, 0.05)) + scale_size_manual(values=c(3, 1)) + scale_color_manual(values=c("red","black"))+ coord_flip() + theme_void() + ggtitle("G1vRev") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1))
# 
# hpm3AvC <- hpm3AvC.GSEA %>% filter(FDR <= 0.05) %>% filter(Collection %in% c("h","c2cgp","c2cp","c5bp", "c5mf", "c5cc"))
# hpm3AvC <- tibble::rownames_to_column(hpm3AvC,"Name")
# ac.gsea.plot <- ggplot() + geom_jitter(data=hpm3AvC, aes(x="Group",y=FDR, color=factor(Hit), alpha=Hit, size=Hit), width=0.1) + scale_alpha_manual(values=c(1, 0.05)) + scale_size_manual(values=c(3, 1)) + scale_color_manual(values=c("red","black"))+ coord_flip() + theme_void() + ggtitle("hpm3AvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1))
# 
# MuscleSvC <- MuscleSvC.GSEA %>% filter(FDR <= 0.05) %>% filter(Collection %in% c("h","c2cgp","c2cp","c5bp", "c5mf", "c5cc"))
# MuscleSvC <- tibble::rownames_to_column(MuscleSvC,"Name")
# sc.gsea.plot <- ggplot() + geom_jitter(data=MuscleSvC, aes(x="Group",y=FDR, color=factor(Hit), alpha=Hit, size=Hit), width=0.1) + scale_alpha_manual(values=c(1, 0.05)) + scale_size_manual(values=c(3, 1)) + scale_color_manual(values=c("red","black"))+ coord_flip() + theme_void() + ggtitle("MuscleSvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1))
# 
# ggarrange(ec.gsea.plot,g1rev.gsea.plot,ac.gsea.plot,sc.gsea.plot, legend = FALSE, ncol=4, nrow=1)
# ```

*GSEA Summary Plots_v2*

```{r, fig.width=10, fig.height=3}
evc <- EvC.GSEA %>% filter(FDR <= 0.05) %>% filter(Collection %in% c("h","c2cgp","c2cp","c5bp", "c5mf", "c5cc"))
evc <- tibble::rownames_to_column(evc,"Name")
evc.gsea.nohit <- evc %>% filter(Hit == "Other")
evc.gsea.hit <- evc %>% filter(Hit == "Hit")
ec.gsea.plot <- ggplot() + geom_jitter(data=evc.gsea.nohit, aes(x="Collection",y=FDR), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=evc.gsea.hit, aes(x="Collection",y=FDR), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("EvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

g1vrev <- G1vRev.GSEA %>% filter(FDR <= 0.05) %>% filter(Collection %in% c("h","c2cgp","c2cp","c5bp", "c5mf", "c5cc"))
g1vrev <- tibble::rownames_to_column(g1vrev,"Name")
g1rev.gsea.nohit <- g1vrev %>% filter(Hit == "Other")
g1rev.gsea.hit <- g1vrev %>% filter(Hit == "Hit")
g1rev.gsea.plot <- ggplot() + geom_jitter(data=g1rev.gsea.nohit, aes(x="Collection",y=FDR), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=g1rev.gsea.hit, aes(x="Collection",y=FDR), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("g1rev") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

hpm3AvC <- hpm3AvC.GSEA %>% filter(FDR <= 0.05) %>% filter(Collection %in% c("h","c2cgp","c2cp","c5bp", "c5mf", "c5cc"))
hpm3AvC <- tibble::rownames_to_column(hpm3AvC,"Name")
ac.gsea.nohit <- hpm3AvC %>% filter(Hit == "Other")
ac.gsea.hit <- hpm3AvC %>% filter(Hit == "Hit")
ac.gsea.plot <- ggplot() + geom_jitter(data=ac.gsea.nohit, aes(x="Collection",y=FDR), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=ac.gsea.hit, aes(x="Collection",y=FDR), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("hpm3.AvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()


MuscleSvC <- MuscleSvC.GSEA %>% filter(FDR <= 0.05) %>% filter(Collection %in% c("h","c2cgp","c2cp","c5bp", "c5mf", "c5cc"))
MuscleSvC <- tibble::rownames_to_column(MuscleSvC,"Name")
sc.gsea.nohit <- MuscleSvC %>% filter(Hit == "Other")
sc.gsea.hit <- MuscleSvC %>% filter(Hit == "Hit")
sc.gsea.plot <- ggplot() + geom_jitter(data=sc.gsea.nohit, aes(x="Collection",y=FDR), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=sc.gsea.hit, aes(x="Collection",y=FDR), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("MuscleSvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

ggarrange(ec.gsea.plot,g1rev.gsea.plot,ac.gsea.plot,sc.gsea.plot, legend = FALSE, ncol=4, nrow=1)
```

*Import DAVID Data*

```{r}
EvC.DAVID <- read.xlsx("../DAVID/evcDEGS.DAVID_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
G1vRev.DAVID <- read.xlsx("../DAVID/g1vRevDEGS.DAVID_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
hpm3AvC.DAVID <- read.xlsx("../DAVID/hpm3avc.DEGS.DAVID_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
MuscleSvC.DAVID <- read.xlsx("../DAVID/muscsvc.DEGS.DAVID_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
```

*DAVID Summary Plots*

# ```{r, fig.width=10, fig.height=3}
# evc <- EvC.DAVID %>% filter(Bonferroni <= 0.05)
# evc <- tibble::rownames_to_column(evc,"Name")
# ec.david.plot <- ggplot() + geom_jitter(data=evc, aes(x="Group",y=FDR, color=factor(Hit), alpha=Hit, size=Hit), width=0.1) + scale_alpha_manual(values=c(1, 0.2)) + scale_size_manual(values=c(3, 2)) + scale_color_manual(values=c("red","black"))+ coord_flip() + theme_void() + ggtitle("EvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1))
# 
# g1vrev <- G1vRev.DAVID %>% filter(Bonferroni <= 0.05)
# g1vrev <- tibble::rownames_to_column(g1vrev,"Name")
# g1rev.david.plot <- ggplot() + geom_jitter(data=g1vrev, aes(x="Group",y=FDR, color=factor(Hit), alpha=Hit, size=Hit), width=0.1) + scale_alpha_manual(values=c(1, 0.2)) + scale_size_manual(values=c(3, 2)) + scale_color_manual(values=c("red","black"))+ coord_flip() + theme_void() + ggtitle("G1vRev") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1))
# 
# hpm3AvC <- hpm3AvC.DAVID %>% filter(Bonferroni <= 0.05)
# hpm3AvC <- tibble::rownames_to_column(hpm3AvC,"Name")
# ac.david.plot <- ggplot() + geom_jitter(data=hpm3AvC, aes(x="Group",y=FDR, color=factor(Hit), alpha=Hit, size=Hit), width=0.1) + scale_alpha_manual(values=c(1, 0.2)) + scale_size_manual(values=c(3, 2)) + scale_color_manual(values=c("red","black"))+ coord_flip() + theme_void() + ggtitle("hpm3AvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1))
# 
# MuscleSvC <- MuscleSvC.DAVID %>% filter(Bonferroni <= 0.05)
# MuscleSvC <- tibble::rownames_to_column(MuscleSvC,"Name")
# sc.david.plot <- ggplot() + geom_jitter(data=MuscleSvC, aes(x="Group",y=FDR, color=factor(Hit), alpha=Hit, size=Hit), width=0.1) + scale_alpha_manual(values=c(1, 0.2)) + scale_size_manual(values=c(3, 2)) + scale_color_manual(values=c("red","black"))+ coord_flip() + theme_void() + ggtitle("MuscleSvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1))
# 
# ggarrange(ec.david.plot,g1rev.david.plot,ac.david.plot,sc.david.plot, legend = FALSE, ncol=4, nrow=1)
# ```

*DAVID Summary Plots_v2*

```{r, fig.width=10, fig.height=3}
evc <- EvC.DAVID %>% filter(Bonferroni <= 0.05)
evc <- tibble::rownames_to_column(evc,"Name")
evc.david.nohit <- evc %>% filter(Hit == "Other")
evc.david.hit <- evc %>% filter(Hit == "Hit")
ec.david.plot <- ggplot() + geom_jitter(data=evc.david.nohit, aes(x="Collection",y=Bonferroni), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=evc.david.hit, aes(x="Collection",y=Bonferroni), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("EvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

g1vrev <- G1vRev.DAVID %>% filter(Bonferroni <= 0.05)
g1vrev <- tibble::rownames_to_column(g1vrev,"Name")
g1rev.david.nohit <- g1vrev %>% filter(Hit == "Other")
g1rev.david.hit <- g1vrev %>% filter(Hit == "Hit")
g1rev.david.plot <- ggplot() + geom_jitter(data=g1rev.david.nohit, aes(x="Collection",y=Bonferroni), color="black", alpha=0.4, size=0.6, width=0.1) + theme_void() + ggtitle("g1rev") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()
#there are no significant hits in g1rev david so the following was extracted
#geom_jitter(data=g1rev.david.hit, aes(x="Collection",y=Bonferroni), color="red", alpha=1, size=2, width=0.1)

hpm3AvC <- hpm3AvC.DAVID %>% filter(Bonferroni <= 0.05)
hpm3AvC <- tibble::rownames_to_column(hpm3AvC,"Name")
ac.david.nohit <- hpm3AvC %>% filter(Hit == "Other")
ac.david.hit <- hpm3AvC %>% filter(Hit == "Hit")
ac.david.plot <- ggplot() + geom_jitter(data=ac.david.nohit, aes(x="Collection",y=Bonferroni), color="black", alpha=0.5, size=0.6, width=0.1) + geom_jitter(data=ac.david.hit, aes(x="Collection",y=Bonferroni), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("hpm3.AvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()


MuscleSvC <- MuscleSvC.DAVID %>% filter(Bonferroni <= 0.05)
MuscleSvC <- tibble::rownames_to_column(MuscleSvC,"Name")
sc.david.nohit <- MuscleSvC %>% filter(Hit == "Other")
sc.david.hit <- MuscleSvC %>% filter(Hit == "Hit")
sc.david.plot <- ggplot() + geom_jitter(data=sc.david.nohit, aes(x="Collection",y=Bonferroni), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=sc.david.hit, aes(x="Collection",y=Bonferroni), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("MuscleSvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

ggarrange(ec.david.plot,g1rev.david.plot,ac.david.plot,sc.david.plot, legend = FALSE, ncol=4, nrow=1)
```

*Import gProfiler Data*

```{r}
EvC.gprofiler <- read.xlsx("../g_profiler/evc.gprofiler_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
G1vRev.gprofiler <- read.xlsx("../g_profiler/g1vrev.gprofiler_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
hpm3AvC.gprofiler <- read.xlsx("../g_profiler/hpm3avc.gprofiler_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
MuscleSvC.gprofiler <- read.xlsx("../g_profiler/muscsvc.gprofiler_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
```

*gProfiler Summary Plots*

# ```{r, fig.width=10, fig.height=3}
# evc <- EvC.gprofiler %>% filter(p_value <= 0.05)
# evc <- tibble::rownames_to_column(evc,"Name")
# ec.gpro.plot <- ggplot() + geom_jitter(data=evc, aes(x="Group",y=p_value, color=factor(Hit), alpha=Hit, size=Hit), width=0.1) + scale_alpha_manual(values=c(1, 0.05)) + scale_size_manual(values=c(3, 1)) + scale_color_manual(values=c("red","black"))+ coord_flip() + theme_void() + ggtitle("EvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1))
# 
# g1vrev <- G1vRev.gprofiler %>% filter(p_value <= 0.05)
# g1vrev <- tibble::rownames_to_column(g1vrev,"Name")
# g1rev.gpro.plot <- ggplot() + geom_jitter(data=g1vrev, aes(x="Group",y=p_value, color=factor(Hit), alpha=Hit, size=Hit), width=0.1) + scale_alpha_manual(values=c(1, 0.2)) + scale_size_manual(values=c(3, 1)) + scale_color_manual(values=c("red","black"))+ coord_flip() + theme_void() + ggtitle("G1vRev") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1))
# 
# hpm3AvC <- hpm3AvC.gprofiler %>% filter(p_value <= 0.05)
# hpm3AvC <- tibble::rownames_to_column(hpm3AvC,"Name")
# ac.gpro.plot <- ggplot() + geom_jitter(data=hpm3AvC, aes(x="Group",y=p_value, color=factor(Hit), alpha=Hit, size=Hit), width=0.1) + scale_alpha_manual(values=c(1, 0.05)) + scale_size_manual(values=c(3, 1)) + scale_color_manual(values=c("red","black"))+ coord_flip() + theme_void() + ggtitle("hpm3AvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1))
# 
# MuscleSvC <- MuscleSvC.gprofiler %>% filter(p_value <= 0.05)
# MuscleSvC <- tibble::rownames_to_column(MuscleSvC,"Name")
# sc.gpro.plot <- ggplot() + geom_jitter(data=MuscleSvC, aes(x="Group",y=p_value, color=factor(Hit), alpha=Hit, size=Hit), width=0.1) + scale_alpha_manual(values=c(1, 0.05)) + scale_size_manual(values=c(3, 1)) + scale_color_manual(values=c("red","black"))+ coord_flip() + theme_void() + ggtitle("MuscleSvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1))
# 
# ggarrange(ec.gpro.plot,g1rev.gpro.plot,ac.gpro.plot,sc.gpro.plot, legend = FALSE, ncol=4, nrow=1)
# ```
*Gprofiler Summary Plots_v2*

```{r, fig.width=10, fig.height=3}
evc <- EvC.gprofiler %>% filter(p_value <= 0.05)
evc <- tibble::rownames_to_column(evc,"Name")
evc.gpro.nohit <- evc %>% filter(Hit == "Other")
evc.gpro.hit <- evc %>% filter(Hit == "Hit")
ec.gpro.plot <- ggplot() + geom_jitter(data=evc.gpro.nohit, aes(x="Collection",y=p_value), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=evc.gpro.hit, aes(x="Collection",y=p_value), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("EvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

g1vrev <- G1vRev.gprofiler %>% filter(p_value <= 0.05)
g1vrev <- tibble::rownames_to_column(g1vrev,"Name")
g1rev.gpro.nohit <- g1vrev %>% filter(Hit == "Other")
g1rev.gpro.hit <- g1vrev %>% filter(Hit == "Hit")
g1rev.gpro.plot <- ggplot() + geom_jitter(data=g1rev.gpro.nohit, aes(x="Collection",y=p_value), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=g1rev.gpro.hit, aes(x="Collection",y=p_value), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("g1rev") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

hpm3AvC <- hpm3AvC.gprofiler %>% filter(p_value <= 0.05)
hpm3AvC <- tibble::rownames_to_column(hpm3AvC,"Name")
ac.gpro.nohit <- hpm3AvC %>% filter(Hit == "Other")
ac.gpro.hit <- hpm3AvC %>% filter(Hit == "Hit")
ac.gpro.plot <- ggplot() + geom_jitter(data=ac.gpro.nohit, aes(x="Collection",y=p_value), color="black", alpha=0.5, size=0.6, width=0.1) + geom_jitter(data=ac.gpro.hit, aes(x="Collection",y=p_value), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("hpm3.AvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()


MuscleSvC <- MuscleSvC.gprofiler %>% filter(p_value <= 0.05)
MuscleSvC <- tibble::rownames_to_column(MuscleSvC,"Name")
sc.gpro.nohit <- MuscleSvC %>% filter(Hit == "Other")
sc.gpro.hit <- MuscleSvC %>% filter(Hit == "Hit")
sc.gpro.plot <- ggplot() + geom_jitter(data=sc.gpro.nohit, aes(x="Collection",y=p_value), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=sc.gpro.hit, aes(x="Collection",y=p_value), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("MuscleSvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

ggarrange(ec.gpro.plot,g1rev.gpro.plot,ac.gpro.plot,sc.gpro.plot, legend = FALSE, ncol=4, nrow=1)
```

*Import Metacore Data*

```{r}
EvC.metacore <- read.xlsx("../shared_data/EvC_metacore_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
G1vRev.metacore <- read.xlsx("../shared_data/G1vRev_metacore_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
hpm3AvC.metacore <- read.xlsx("../shared_data/hpm3_AvC_metacore_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
MuscleSvC.metacore <- read.xlsx("../shared_data/Muscle_SkeletalvsCardiac_metacore_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
```

*Metacore Summary Plots*

# ```{r, fig.width=10, fig.height=3}
# evc <- EvC.metacore %>% filter(FDR <= 0.05)
# evc <- tibble::rownames_to_column(evc,"Name")
# ec.meta.plot <- ggplot() + geom_jitter(data=evc, aes(x="Group",y=FDR, color=factor(Hit), alpha=Hit, size=Hit), width=0.1) + scale_alpha_manual(values=c(1, 0.2)) + scale_size_manual(values=c(3, 1)) + scale_color_manual(values=c("red","black"))+ coord_flip() + theme_void() + ggtitle("EvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1))
# 
# #plotting parameters altered on account of no significant pathways in group
# g1vrev <- G1vRev.metacore %>% filter(FDR <= 0.05)
# g1vrev <- tibble::rownames_to_column(g1vrev,"Name")
# g1rev.meta.plot <- ggplot() + geom_jitter(data=g1vrev, aes(x="Group",y=FDR, color=factor(Hit), alpha=Hit, size=Hit), width=0.1) + scale_alpha_manual(values=c(0.2, 1)) + scale_size_manual(values=c(1, 3)) + scale_color_manual(values=c("black","red"))+ coord_flip() + theme_void() + ggtitle("G1vRev") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1))
# 
# hpm3AvC <- hpm3AvC.metacore %>% filter(FDR <= 0.05)
# hpm3AvC <- tibble::rownames_to_column(hpm3AvC,"Name")
# ac.meta.plot <- ggplot() + geom_jitter(data=hpm3AvC, aes(x="Group",y=FDR, color=factor(Hit), alpha=Hit, size=Hit), width=0.1) + scale_alpha_manual(values=c(1, 0.2)) + scale_size_manual(values=c(3, 1)) + scale_color_manual(values=c("red","black"))+ coord_flip() + theme_void() + ggtitle("hpm3AvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1))
# 
# MuscleSvC <- MuscleSvC.metacore %>% filter(FDR <= 0.05)
# MuscleSvC <- tibble::rownames_to_column(MuscleSvC,"Name")
# sc.meta.plot <- ggplot() + geom_jitter(data=MuscleSvC, aes(x="Group",y=FDR, color=factor(Hit), alpha=Hit, size=Hit), width=0.1) + scale_alpha_manual(values=c(1, 0.2)) + scale_size_manual(values=c(3, 1)) + scale_color_manual(values=c("red","black"))+ coord_flip() + theme_void() + ggtitle("MuscleSvC")+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1))
# 
# ggarrange(ec.meta.plot,g1rev.meta.plot,ac.meta.plot,sc.meta.plot, legend = FALSE, ncol=4, nrow=1)
# ```

*Metacore Summary Plots_v2*

```{r, fig.width=10, fig.height=3}
evc <- EvC.metacore %>% filter(FDR <= 0.05)     
evc <- tibble::rownames_to_column(evc,"Name")
evc.mcore.nohit <- evc %>% filter(Hit == "Other")
evc.mcore.hit <- evc %>% filter(Hit == "Hit")
ec.mcore.plot <- ggplot() + geom_jitter(data=evc.mcore.nohit, aes(x="Collection",y=FDR), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=evc.mcore.hit, aes(x="Collection",y=FDR), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("EvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()        

g1vrev <- G1vRev.metacore %>% filter(FDR <= 0.05)     
g1vrev <- tibble::rownames_to_column(g1vrev,"Name")
g1rev.mcore.nohit <- g1vrev %>% filter(Hit == "Other")
g1rev.mcore.hit <- g1vrev %>% filter(Hit == "Hit")
g1rev.mcore.plot <- ggplot() + geom_jitter(data=g1rev.mcore.nohit, aes(x="Collection",y=FDR), color="black", alpha=0.4, size=0.6, width=0.1) + theme_void() + ggtitle("g1rev") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

#no significant g1rev hits for metacore so this line was extracted
#geom_jitter(data=g1rev.mcore.hit, aes(x="Collection",y=FDR), color="red", alpha=1, size=2, width=0.1)

hpm3AvC <- hpm3AvC.metacore %>% filter(FDR <= 0.05)     
hpm3AvC <- tibble::rownames_to_column(hpm3AvC,"Name")
ac.mcore.nohit <- hpm3AvC %>% filter(Hit == "Other")
ac.mcore.hit <- hpm3AvC %>% filter(Hit == "Hit")
ac.mcore.plot <- ggplot() + geom_jitter(data=ac.mcore.nohit, aes(x="Collection",y=FDR), color="black", alpha=0.5, size=0.6, width=0.1) + geom_jitter(data=ac.mcore.hit, aes(x="Collection",y=FDR), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("hpm3.AvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip() 

MuscleSvC <- MuscleSvC.metacore %>% filter(FDR <= 0.05)     
MuscleSvC <- tibble::rownames_to_column(MuscleSvC,"Name")
sc.mcore.nohit <- MuscleSvC %>% filter(Hit == "Other")
sc.mcore.hit <- MuscleSvC %>% filter(Hit == "Hit")
sc.mcore.plot <- ggplot() + geom_jitter(data=sc.mcore.nohit, aes(x="Collection",y=FDR), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=sc.mcore.hit, aes(x="Collection",y=FDR), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("MuscleSvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()

ggarrange(ec.mcore.plot,g1rev.mcore.plot,ac.mcore.plot,sc.mcore.plot, legend = FALSE, ncol=4, nrow=1)
```


*Import IPA Data*
```{r}
EvC.ipa <- read.xlsx("../shared_data/EvC_ipa_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
G1vRev.ipa <- read.xlsx("../shared_data/G1vRev_ipa_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
hpm3AvC.ipa <- read.xlsx("../shared_data/hpm3_AvC_ipa_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
MuscleSvC.ipa <- read.xlsx("../shared_data/Muscle_SkeletalvsCardiac_ipa_withOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
```

*IPA Summary Plots*

# ```{r, fig.width=10, fig.height=3}
# evc <- EvC.ipa %>% filter(p_value <= 0.05)
# evc <- tibble::rownames_to_column(evc,"Name")
# ec.ipa.plot <- ggplot() + geom_jitter(data=evc, aes(x="Group",y=p_value, color=factor(Hit), alpha=Hit, size=Hit), width=0.1) + scale_alpha_manual(values=c(1, 0.2)) + scale_size_manual(values=c(3, 1)) + scale_color_manual(values=c("red","black"))+ coord_flip() + theme_void() + ggtitle("EvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1))
# 
# g1vrev <- G1vRev.ipa %>% filter(p_value <= 0.05)
# g1vrev <- tibble::rownames_to_column(g1vrev,"Name")
# g1rev.ipa.plot <- ggplot() + geom_jitter(data=g1vrev, aes(x="Group",y=p_value, color=factor(Hit), alpha=Hit, size=Hit), width=0.1) + scale_alpha_manual(values=c(1, 0.2)) + scale_size_manual(values=c(3, 1)) + scale_color_manual(values=c("red","black"))+ coord_flip() + theme_void() + ggtitle("G1vRev") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1))
# 
# hpm3AvC <- hpm3AvC.ipa %>% filter(p_value <= 0.05)
# hpm3AvC <- tibble::rownames_to_column(hpm3AvC,"Name")
# ac.ipa.plot <- ggplot() + geom_jitter(data=hpm3AvC, aes(x="Group",y=p_value, color=factor(Hit), alpha=Hit, size=Hit), width=0.1) + scale_alpha_manual(values=c(1, 0.2)) + scale_size_manual(values=c(3, 1)) + scale_color_manual(values=c("red","black"))+ coord_flip() + theme_void() + ggtitle("hpm3AvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1))
# 
# MuscleSvC <- MuscleSvC.ipa %>% filter(p_value <= 0.05)
# MuscleSvC <- tibble::rownames_to_column(MuscleSvC,"Name")
# sc.ipa.plot <- ggplot() + geom_jitter(data=MuscleSvC, aes(x="Group",y=p_value, color=factor(Hit), alpha=Hit, size=Hit), width=0.1) + scale_alpha_manual(values=c(1, 0.2)) + scale_size_manual(values=c(3, 1)) + scale_color_manual(values=c("red","black"))+ coord_flip() + theme_void() + ggtitle("MuscleSvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1))
# 
# ggarrange(ec.ipa.plot,g1rev.ipa.plot,ac.ipa.plot,sc.ipa.plot, legend = FALSE, ncol=4, nrow=1)
# ```

```{r, fig.width=10, fig.height=3}
evc <- EvC.ipa %>% filter(p_value <= 0.05)          
evc <- tibble::rownames_to_column(evc,"Name")
evc.ipa.nohit <- evc %>% filter(Hit == "Other")  
evc.ipa.hit <- evc %>% filter(Hit == "Hit")  
ec.ipa.plot <- ggplot() + geom_jitter(data=evc.ipa.nohit, aes(x="Collection",y=p_value), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=evc.ipa.hit, aes(x="Collection",y=p_value), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("EvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()              

g1vrev <- G1vRev.ipa %>% filter(p_value <= 0.05)          
g1vrev <- tibble::rownames_to_column(g1vrev,"Name")
g1rev.ipa.nohit <- g1vrev %>% filter(Hit == "Other")  
g1rev.ipa.hit <- g1vrev %>% filter(Hit == "Hit")  
g1rev.ipa.plot <- ggplot() + geom_jitter(data=g1rev.ipa.nohit, aes(x="Collection",y=p_value), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=g1rev.ipa.hit, aes(x="Collection",y=p_value), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("g1rev") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()              

hpm3AvC <- hpm3AvC.ipa %>% filter(p_value <= 0.05)          
hpm3AvC <- tibble::rownames_to_column(hpm3AvC,"Name")
ac.ipa.nohit <- hpm3AvC %>% filter(Hit == "Other")  
ac.ipa.hit <- hpm3AvC %>% filter(Hit == "Hit")  
ac.ipa.plot <- ggplot() + geom_jitter(data=ac.ipa.nohit, aes(x="Collection",y=p_value), color="black", alpha=0.5, size=0.6, width=0.1) + geom_jitter(data=ac.ipa.hit, aes(x="Collection",y=p_value), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("hpm3.AvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()              


MuscleSvC <- MuscleSvC.ipa %>% filter(p_value <= 0.05)          
MuscleSvC <- tibble::rownames_to_column(MuscleSvC,"Name")
sc.ipa.nohit <- MuscleSvC %>% filter(Hit == "Other")  
sc.ipa.hit <- MuscleSvC %>% filter(Hit == "Hit")  
sc.ipa.plot <- ggplot() + geom_jitter(data=sc.ipa.nohit, aes(x="Collection",y=p_value), color="black", alpha=0.4, size=0.6, width=0.1) + geom_jitter(data=sc.ipa.hit, aes(x="Collection",y=p_value), color="red", alpha=1, size=2, width=0.1) + theme_void() + ggtitle("MuscleSvC") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(color = "black", size=1)) + coord_flip()              

ggarrange(ec.ipa.plot,g1rev.ipa.plot,ac.ipa.plot,sc.ipa.plot, legend = FALSE, ncol=4, nrow=1)        
```

*Import iPathway Data*
*iPathway Summary Plots*

*Old Processing*
```{r}
#eVcMetacore <- read.xlsx("PPAR_EvC_MetacorePlusOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
#eVcGSEA <- read.xlsx("EvC_GSEAv4_PlusOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
#eVcDAVID.degs <- read.xlsx("../DAVID/EvC_degs_DAVIDPlusOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
#eVcDAVID.upE <- read.xlsx("EvC_upE_DAVIDPlusOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
#eVcDAVID.upC <- read.xlsx("EvC_upC_DAVIDPlusOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
#eVcgprofiler.degs <- read.xlsx("EvC_degs_gProfiler_PlusOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
#g1vRev.GSEA <- read.xlsx("../shared_data/G1vRev_GSEAv4_plusOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
#g1vRev.gprofiler <- read.xlsx("../g_profiler/g1vrev.std.bg.gprofilerPlusOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
#g1vRev.DAVID <- read.xlsx("../DAVID/g1vRev.upRev.0.58FC.DAVID.PlusOverlaps.xlsx", colNames=TRUE, rowNames=TRUE)
```

*Plot EvC data GSEA for gene sets containing PPAR*

```{r}
#pvals <- gsea %>% filter(`PPAR.E.C.FDR.q-val` <= 0.05 & FractionMatches < 0.1)
#pvals <- eVc %>% filter(`EvC.norm.stat.FDR.q-val` <= 0.05)
#pvals <- tibble::rownames_to_column(pvals,"SetName")
#ppar <- pvals %>% select(SetName,Collection,FractionMatches,`EvC.norm.stat.FDR.q-val`)
#ppar <- ppar %>% mutate(relevant=ifelse(grepl("_PPAR", SetName), "Hit", "Other"))
#ggplot() + geom_jitter(data=ppar, aes(x="Group",y=`EvC.norm.stat.FDR.q-val`, color=factor(relevant), alpha=relevant, size=relevant), width=0.1) + scale_alpha_manual(values=c(1, 0.1)) + scale_size_manual(values=c(3, 1)) + scale_color_manual(values=c("red","black"))+ coord_flip() + theme_void()
#ggplot() + geom_point(data=ppar, aes(x="Group",y=`EvC.norm.stat.FDR.q-val`, color=factor(relevant), alpha=relevant, size=relevant)) + scale_alpha_manual(values=c(1, 0.1)) + scale_size_manual(values=c(3, 1)) + scale_color_manual(values=c("red","black"))+ coord_flip()
```


*Plotting multicolor G1vRev gprofiler results*

#```{r, fig.width=3}
#pvals <- g1vRev.gprofiler %>% filter(p_value <= 0.05)
#pvals <- tibble::rownames_to_column(pvals,"Term")
#ggplot() + geom_jitter(data=pvals, aes(x="Group",y=p_value, color=factor(Hit), alpha=Hit, size=Hit), width=0.1) + scale_alpha_manual(values=c(1, 0.2, 0.05)) + #scale_size_manual(values=c(3, 1, 1)) + scale_color_manual(values=c("red","blue","black"))+ coord_flip() + theme_void()
#ggplot() + geom_point(data=pvals, aes(x="Group",y=FDR, , color=factor(relevant), alpha=relevant, size=relevant)) + scale_alpha_manual(values=c(1, 0.05)) + #scale_size_manual(values=c(3, 1)) + scale_color_manual(values=c("red","black"))+ coord_flip()
#```

*Plotting the full EvC GSEA results*

```{r, fig.width=12, fig.height=6}
pvals <- EvC.GSEA  %>% filter(Collection %in% c("h","c2cgp","c2cp","c5bp", "c5mf", "c5cc"))
pvals <- tibble::rownames_to_column(pvals,"Term")
pvals.nohit <- pvals %>% filter(Hit == "Other")
pvals.hit <- pvals %>% filter(Hit == "Hit")

ggplot() + geom_jitter(data=pvals.nohit, aes(x=Collection,y=FDR), color="black", alpha=0.3, size=0.6, width=0.1) + geom_jitter(data=pvals.hit, aes(x=Collection,y=FDR), color="red", alpha=1, size=2, width=0.1) + theme_bw() + coord_flip()
```

## write session info*

```{r}
sessionInfo()
writeLines(capture.output(sessionInfo()), "sessionInfo.txt")
```