---
title: "DAVID Work - ABRF GBIRG"
author: "Charlie Whittaker"
date: "12/20/2020"
output: 
  html_document: default
  html_notebook: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*Load libraries*

```{r, warning=FALSE,error=FALSE,message=FALSE}
library(openxlsx)
library(ggplot2)
library(tidyverse)
library(RDAVIDWebService)
library(org.Hs.eg.db)
library(org.Mm.eg.db)
```

*Import Biological Concept Data*

```{r}
PPAR <- read.xlsx("../shared_data/KEGG_PPAR_SIGNALING_PATHWAY_withMouse.xlsx", colNames=TRUE, rowNames=FALSE)
E2F <- read.xlsx("../shared_data/HALLMARK_E2F_TARGETS.xlsx", colNames=TRUE, rowNames=FALSE)
TNF  <- read.xlsx("../shared_data/HALLMARK_TNFA_SIGNALING_VIA_NFKB.xlsx", colNames=TRUE, rowNames=FALSE)
MUSC <- read.xlsx("../shared_data/GO_SKELETAL_MUSCLE_CONTRACTION.xlsx", colNames=TRUE, rowNames=FALSE)
```

*Run DAVID on Biological Concept Data*

```{r}
hsPPAR <- na.omit(PPAR$HGNCSym)
mmPPAR <- na.omit(PPAR$MGISym)

mmPPAR.ensID <- mapIds(org.Mm.eg.db, keys = mmPPAR, keytype = "SYMBOL", column="ENSEMBL")
E2F.ensID <- mapIds(org.Hs.eg.db, keys = E2F$HALLMARK_E2F_TARGETS, keytype = "SYMBOL", column="ENSEMBL")
TNF.ensID <- mapIds(org.Hs.eg.db, keys = TNF$HALLMARK_TNFA_SIGNALING_VIA_NFKB, keytype = "SYMBOL", column="ENSEMBL")
MUSC.ensID <- mapIds(org.Hs.eg.db, keys = MUSC$GO_SKELETAL_MUSCLE_CONTRACTION, keytype = "SYMBOL", column="ENSEMBL")
##
david<-DAVIDWebService$new(email="charliew@mit.edu", url="https://david.ncifcrf.gov/webservice/services/DAVIDWebService")

result<-addList(david, mmPPAR.ensID, idType="ENSEMBL_GENE_ID", 
                listName="mmPPAR", listType="Gene")

setAnnotationCategories(david, c("GOTERM_BP_DIRECT","GOTERM_MF_DIRECT", "GOTERM_CC_DIRECT", 
                                 "KEGG_PATHWAY", "REACTOME_PATHWAY","BIOCARTA"))

setCurrentGeneListPosition(david, 1)
setCurrentBackgroundPosition(david, 1)
setCurrentSpecies(david, 1)
getFunctionalAnnotationChartFile(david, "PPAR.DAVID.txt")
##
david<-DAVIDWebService$new(email="charliew@mit.edu", url="https://david.ncifcrf.gov/webservice/services/DAVIDWebService")

result<-addList(david, E2F.ensID, idType="ENSEMBL_GENE_ID", 
                listName="E2F", listType="Gene")

setAnnotationCategories(david, c("GOTERM_BP_DIRECT","GOTERM_MF_DIRECT", "GOTERM_CC_DIRECT", 
                                 "KEGG_PATHWAY", "REACTOME_PATHWAY","BIOCARTA"))

setCurrentGeneListPosition(david, 1)
setCurrentBackgroundPosition(david, 1)
setCurrentSpecies(david, 1)
getFunctionalAnnotationChartFile(david, "E2F.DAVID.txt")
##
david<-DAVIDWebService$new(email="charliew@mit.edu", url="https://david.ncifcrf.gov/webservice/services/DAVIDWebService")

result<-addList(david, TNF.ensID, idType="ENSEMBL_GENE_ID", 
                listName="TNF", listType="Gene")

setAnnotationCategories(david, c("GOTERM_BP_DIRECT","GOTERM_MF_DIRECT", "GOTERM_CC_DIRECT", 
                                 "KEGG_PATHWAY", "REACTOME_PATHWAY","BIOCARTA"))

setCurrentGeneListPosition(david, 1)
setCurrentBackgroundPosition(david, 1)
setCurrentSpecies(david, 1)
getFunctionalAnnotationChartFile(david, "TNF.DAVID.txt")
##
david<-DAVIDWebService$new(email="charliew@mit.edu", url="https://david.ncifcrf.gov/webservice/services/DAVIDWebService")

result<-addList(david, MUSC.ensID, idType="ENSEMBL_GENE_ID", 
                listName="Musc", listType="Gene")

setAnnotationCategories(david, c("GOTERM_BP_DIRECT","GOTERM_MF_DIRECT", "GOTERM_CC_DIRECT", 
                                 "KEGG_PATHWAY", "REACTOME_PATHWAY","BIOCARTA"))

setCurrentGeneListPosition(david, 1)
setCurrentBackgroundPosition(david, 1)
setCurrentSpecies(david, 1)
getFunctionalAnnotationChartFile(david, "MUSC.DAVID.txt")
```

*Load Differential Expression Results for Comparisons and run DAVID using default backgrounds*

```{r}
evc <- read.xlsx("../shared_data/EvC_data.xlsx", colNames=TRUE, rowNames=TRUE)
g1vrev <- read.xlsx("../shared_data/G1vRev_data.xlsx", colNames=TRUE, rowNames=TRUE)
hmp3avc <- read.xlsx("../shared_data/hpm3_AvC_data.xlsx", colNames=TRUE, rowNames=TRUE)
muscsvc <- read.xlsx("../shared_data/musc_SkeVHeart.xlsx", colNames=TRUE, rowNames=TRUE)

#When re-running on 1/28/21 to capture all results instead of those with EASE < 0.1
#webservices rejected all lists > 3000 length. 
#due to this, I needed to use default species background and had to be more stringent with muscle comparison (2FC)
#this work-around failed as well... maybe something wrong with the tool?

evc <- tibble::rownames_to_column(evc,"Gene")
evc.degs <- evc %>% filter(adp <= 0.05 & abs(logFC) >= 1)
#evc.bkground <- evc %>% dplyr::select(c("Gene"))

evc.degs.ensID <- na.omit(mapIds(org.Mm.eg.db, keys = evc.degs$Gene, keytype = "SYMBOL", column="ENSEMBL"))
#evc.bkground.ensID <- na.omit(mapIds(org.Mm.eg.db, keys = evc.bkground$Gene, keytype = "SYMBOL", column="ENSEMBL"))

david<-DAVIDWebService$new(email="charliew@mit.edu", url="https://david.ncifcrf.gov/webservice/services/DAVIDWebService")

result<-addList(david, evc.degs.ensID, idType="ENSEMBL_GENE_ID", 
                listName="evc.degs", listType="Gene")

#result<-addList(david, evc.bkground.ensID, idType="ENSEMBL_GENE_ID", 
#                listName="evc.bkground", listType="Background")

setAnnotationCategories(david, c("GOTERM_BP_DIRECT","GOTERM_MF_DIRECT", "GOTERM_CC_DIRECT", 
                                 "KEGG_PATHWAY", "REACTOME_PATHWAY","BIOCARTA"))

setCurrentGeneListPosition(david, 1)
setCurrentBackgroundPosition(david, 1)
setCurrentSpecies(david, 1)

getFunctionalAnnotationChartFile(david, threshold=1,"evcDEGS.DAVID_all.txt")

###
g1vrev <- tibble::rownames_to_column(g1vrev,"Gene")
g1vrev.degs <- g1vrev %>% filter(adp <= 0.05 & abs(logFC) >= 1)
#g1vrev.bkground <- g1vrev %>% dplyr::select(c("Gene"))

g1vrev.degs.ensID <- na.omit(mapIds(org.Hs.eg.db, keys = g1vrev.degs$Gene, keytype = "SYMBOL", column="ENSEMBL"))
#g1vrev.bkground.ensID <- na.omit(mapIds(org.Hs.eg.db, keys = g1vrev.bkground$Gene, keytype = "SYMBOL", column="ENSEMBL"))

david<-DAVIDWebService$new(email="charliew@mit.edu", url="https://david.ncifcrf.gov/webservice/services/DAVIDWebService")

result<-addList(david, g1vrev.degs.ensID, idType="ENSEMBL_GENE_ID", 
                listName="g1vrev.degs", listType="Gene")

#result<-addList(david, g1vrev.bkground.ensID, idType="ENSEMBL_GENE_ID", 
#                listName="g1vrev.bkground", listType="Background")

setAnnotationCategories(david, c("GOTERM_BP_DIRECT","GOTERM_MF_DIRECT", "GOTERM_CC_DIRECT", 
                                 "KEGG_PATHWAY", "REACTOME_PATHWAY","BIOCARTA"))

setCurrentGeneListPosition(david, 1)
setCurrentBackgroundPosition(david, 1)
setCurrentSpecies(david, 1)

getFunctionalAnnotationChartFile(david, threshold=1, "g1vRev.DEGS.1.DAVID.txt")
###
hmp3avc <- tibble::rownames_to_column(hmp3avc,"Gene")
hmp3avc.degs <- hmp3avc %>% filter(adp <= 0.05 & abs(logFC) >= 1)
#hmp3avc.bkground <- hmp3avc %>% dplyr::select(c("Gene"))

hmp3avc.degs.ensID <- na.omit(mapIds(org.Hs.eg.db, keys = hmp3avc.degs$Gene, keytype = "SYMBOL", column="ENSEMBL"))
#hmp3avc.bkground.ensID <- na.omit(mapIds(org.Hs.eg.db, keys = hmp3avc.bkground$Gene, keytype = "SYMBOL", column="ENSEMBL"))

david<-DAVIDWebService$new(email="charliew@mit.edu", url="https://david.ncifcrf.gov/webservice/services/DAVIDWebService")

result<-addList(david, hmp3avc.degs.ensID, idType="ENSEMBL_GENE_ID", 
                listName="hmp3avc.degs", listType="Gene")

#result<-addList(david, hmp3avc.bkground.ensID, idType="ENSEMBL_GENE_ID", 
#                listName="hmp3avc.bkground", listType="Background")

setAnnotationCategories(david, c("GOTERM_BP_DIRECT","GOTERM_MF_DIRECT", "GOTERM_CC_DIRECT", 
                                 "KEGG_PATHWAY", "REACTOME_PATHWAY","BIOCARTA"))

setCurrentGeneListPosition(david, 1)
setCurrentBackgroundPosition(david, 1)
setCurrentSpecies(david, 1)

getFunctionalAnnotationChartFile(david, threshold=1, "hpm3avc.DEGS.DAVID_all.txt")

###
muscsvc <- tibble::rownames_to_column(muscsvc,"Gene")
muscsvc.degs <- muscsvc %>% filter(adp <= 0.05 & abs(logFC) >= 1)
#muscsvc.bkground <- muscsvc %>% dplyr::select(c("Gene"))

muscsvc.degs.ensID <- na.omit(mapIds(org.Hs.eg.db, keys = muscsvc.degs$Gene, keytype = "SYMBOL", column="ENSEMBL"))
#muscsvc.bkground.ensID <- na.omit(mapIds(org.Hs.eg.db, keys = muscsvc.bkground$Gene, keytype = "SYMBOL", column="ENSEMBL"))

david<-DAVIDWebService$new(email="charliew@mit.edu", url="https://david.ncifcrf.gov/webservice/services/DAVIDWebService")

result<-addList(david, muscsvc.degs.ensID, idType="ENSEMBL_GENE_ID", 
                listName="muscsvc.degs", listType="Gene")

#result<-addList(david, muscsvc.bkground.ensID, idType="ENSEMBL_GENE_ID", 
#                listName="muscsvc.bkground", listType="Background")

setAnnotationCategories(david, c("GOTERM_BP_DIRECT","GOTERM_MF_DIRECT", "GOTERM_CC_DIRECT", 
                                 "KEGG_PATHWAY", "REACTOME_PATHWAY","BIOCARTA"))

setCurrentGeneListPosition(david, 1)
setCurrentBackgroundPosition(david, 1)
setCurrentSpecies(david, 1)

getFunctionalAnnotationChartFile(david, threshold=1, "muscsvc.DEGS.DAVID_all.txt")
```
*Load Differential Expression Results for Comparisons and run DAVID using experiment-specific backgrounds*
*This fails on 1/28/21 when trying to load the large lists but the exact code worked a month ago*

```{r}
evc <- read.xlsx("../shared_data/EvC_data.xlsx", colNames=TRUE, rowNames=TRUE)
g1vrev <- read.xlsx("../shared_data/G1vRev_data.xlsx", colNames=TRUE, rowNames=TRUE)
hmp3avc <- read.xlsx("../shared_data/hpm3_AvC_data.xlsx", colNames=TRUE, rowNames=TRUE)
muscsvc <- read.xlsx("../shared_data/musc_SkeVHeart.xlsx", colNames=TRUE, rowNames=TRUE)

evc <- tibble::rownames_to_column(evc,"Gene")
evc.degs <- evc %>% filter(adp <= 0.05 & abs(logFC) >= 1)
evc.bkground <- evc %>% dplyr::select(c("Gene"))

evc.degs.ensID <- na.omit(mapIds(org.Mm.eg.db, keys = evc.degs$Gene, keytype = "SYMBOL", column="ENSEMBL"))
evc.bkground.ensID <- na.omit(mapIds(org.Mm.eg.db, keys = evc.bkground$Gene, keytype = "SYMBOL", column="ENSEMBL"))

david<-DAVIDWebService$new(email="charliew@mit.edu", url="https://david.ncifcrf.gov/webservice/services/DAVIDWebService")

result<-addList(david, evc.degs.ensID, idType="ENSEMBL_GENE_ID", 
                listName="evc.degs", listType="Gene")

result<-addList(david, evc.bkground.ensID, idType="ENSEMBL_GENE_ID", 
                listName="evc.bkground", listType="Background")

setAnnotationCategories(david, c("GOTERM_BP_DIRECT","GOTERM_MF_DIRECT", "GOTERM_CC_DIRECT", 
                                 "KEGG_PATHWAY", "REACTOME_PATHWAY","BIOCARTA"))

setCurrentGeneListPosition(david, 1)
setCurrentBackgroundPosition(david, 2)
setCurrentSpecies(david, 1)

getFunctionalAnnotationChartFile(david, threshold=1,"evcDEGS.DAVID_thresh2.txt")

###
g1vrev <- tibble::rownames_to_column(g1vrev,"Gene")
g1vrev.degs <- g1vrev %>% filter(adp <= 0.05 & abs(logFC) >= 1)
g1vrev.bkground <- g1vrev %>% dplyr::select(c("Gene"))

g1vrev.degs.ensID <- na.omit(mapIds(org.Hs.eg.db, keys = g1vrev.degs$Gene, keytype = "SYMBOL", column="ENSEMBL"))
g1vrev.bkground.ensID <- na.omit(mapIds(org.Hs.eg.db, keys = g1vrev.bkground$Gene, keytype = "SYMBOL", column="ENSEMBL"))

david<-DAVIDWebService$new(email="charliew@mit.edu", url="https://david.ncifcrf.gov/webservice/services/DAVIDWebService")

result<-addList(david, g1vrev.degs.ensID, idType="ENSEMBL_GENE_ID", 
                listName="g1vrev.degs", listType="Gene")

result<-addList(david, g1vrev.bkground.ensID, idType="ENSEMBL_GENE_ID", 
                listName="g1vrev.bkground", listType="Background")

setAnnotationCategories(david, c("GOTERM_BP_DIRECT","GOTERM_MF_DIRECT", "GOTERM_CC_DIRECT", 
                                 "KEGG_PATHWAY", "REACTOME_PATHWAY","BIOCARTA"))

setCurrentGeneListPosition(david, 1)
setCurrentBackgroundPosition(david, 2)
setCurrentSpecies(david, 1)

getFunctionalAnnotationChartFile(david, threshold=1, "g1vRevDEGS.DAVID_thresh2.txt")
###
hmp3avc <- tibble::rownames_to_column(hmp3avc,"Gene")
hmp3avc.degs <- hmp3avc %>% filter(adp <= 0.05 & abs(logFC) >= 1)
hmp3avc.bkground <- hmp3avc %>% dplyr::select(c("Gene"))

hmp3avc.degs.ensID <- na.omit(mapIds(org.Hs.eg.db, keys = hmp3avc.degs$Gene, keytype = "SYMBOL", column="ENSEMBL"))
hmp3avc.bkground.ensID <- na.omit(mapIds(org.Hs.eg.db, keys = hmp3avc.bkground$Gene, keytype = "SYMBOL", column="ENSEMBL"))

david<-DAVIDWebService$new(email="charliew@mit.edu", url="https://david.ncifcrf.gov/webservice/services/DAVIDWebService")

result<-addList(david, hmp3avc.degs.ensID, idType="ENSEMBL_GENE_ID", 
                listName="hmp3avc.degs", listType="Gene")

result<-addList(david, hmp3avc.bkground.ensID, idType="ENSEMBL_GENE_ID", 
                listName="hmp3avc.bkground", listType="Background")

setAnnotationCategories(david, c("GOTERM_BP_DIRECT","GOTERM_MF_DIRECT", "GOTERM_CC_DIRECT", 
                                 "KEGG_PATHWAY", "REACTOME_PATHWAY","BIOCARTA"))

setCurrentGeneListPosition(david, 1)
setCurrentBackgroundPosition(david, 2)
setCurrentSpecies(david, 1)

getFunctionalAnnotationChartFile(david, threshold=1, "hpm3avc.DEGS.DAVID_thresh2.txt")

###
muscsvc <- tibble::rownames_to_column(muscsvc,"Gene")
muscsvc.degs <- muscsvc %>% filter(adp <= 0.05 & abs(logFC) >= 1)
muscsvc.bkground <- muscsvc %>% dplyr::select(c("Gene"))

muscsvc.degs.ensID <- na.omit(mapIds(org.Hs.eg.db, keys = muscsvc.degs$Gene, keytype = "SYMBOL", column="ENSEMBL"))
muscsvc.bkground.ensID <- na.omit(mapIds(org.Hs.eg.db, keys = muscsvc.bkground$Gene, keytype = "SYMBOL", column="ENSEMBL"))

david<-DAVIDWebService$new(email="charliew@mit.edu", url="https://david.ncifcrf.gov/webservice/services/DAVIDWebService")

result<-addList(david, muscsvc.degs.ensID, idType="ENSEMBL_GENE_ID", 
                listName="muscsvc.degs", listType="Gene")

result<-addList(david, muscsvc.bkground.ensID, idType="ENSEMBL_GENE_ID", 
                listName="muscsvc.bkground", listType="Background")

setAnnotationCategories(david, c("GOTERM_BP_DIRECT","GOTERM_MF_DIRECT", "GOTERM_CC_DIRECT", 
                                 "KEGG_PATHWAY", "REACTOME_PATHWAY","BIOCARTA"))

setCurrentGeneListPosition(david, 1)
setCurrentBackgroundPosition(david, 2)
setCurrentSpecies(david, 1)

getFunctionalAnnotationChartFile(david, threshold=1, "muscsvc.DEGS.DAVID_thresh2.txt")
```

*Rerun E2F set with GO _ALL Annotation Categories to facilitate comparison with other tools*
```{r}
E2F.ensID <- mapIds(org.Hs.eg.db, keys = E2F$HALLMARK_E2F_TARGETS, keytype = "SYMBOL", column="ENSEMBL")

david<-DAVIDWebService$new(email="charliew@mit.edu", url="https://david.ncifcrf.gov/webservice/services/DAVIDWebService")

result<-addList(david, E2F.ensID, idType="ENSEMBL_GENE_ID", 
                listName="E2F", listType="Gene")

setAnnotationCategories(david, c("GOTERM_BP_ALL","GOTERM_MF_ALL", "GOTERM_CC_ALL", 
                                 "KEGG_PATHWAY", "REACTOME_PATHWAY","BIOCARTA"))

setCurrentGeneListPosition(david, 1)
setCurrentBackgroundPosition(david, 1)
setCurrentSpecies(david, 1)
getFunctionalAnnotationChartFile(david, "E2F.ALL.DAVID.txt")
```

*Rerun G1rev with default background, relaxed 0.58 FC cut-off*

```{r}
g1vrev <- read.xlsx("../shared_data/G1vRev_data.xlsx", colNames=TRUE, rowNames=TRUE)
g1vrev <- tibble::rownames_to_column(g1vrev,"Gene")

g1vrev.neg.degs <- g1vrev %>% filter(adp <= 0.05 & abs(logFC) >= 0.58)
#g1vrev.bkground <- g1vrev %>% dplyr::select(c("Gene"))

g1vrev.neg.degs.ensID <- na.omit(mapIds(org.Hs.eg.db, keys = g1vrev.neg.degs$Gene, keytype = "SYMBOL", column="ENSEMBL"))
#g1vrev.bkground.ensID <- na.omit(mapIds(org.Hs.eg.db, keys = g1vrev.bkground$Gene, keytype = "SYMBOL", column="ENSEMBL"))

david<-DAVIDWebService$new(email="charliew@mit.edu", url="https://david.ncifcrf.gov/webservice/services/DAVIDWebService")

result<-addList(david, g1vrev.neg.degs.ensID, idType="ENSEMBL_GENE_ID", 
                listName="g1vrev.neg.degs", listType="Gene")

#result<-addList(david, g1vrev.bkground.ensID, idType="ENSEMBL_GENE_ID", 
#                listName="g1vrev.bkground", listType="Background")

setAnnotationCategories(david, c("GOTERM_BP_DIRECT","GOTERM_MF_DIRECT", "GOTERM_CC_DIRECT", 
                                 "KEGG_PATHWAY", "REACTOME_PATHWAY","BIOCARTA"))

setCurrentGeneListPosition(david, 1)
setCurrentBackgroundPosition(david, 1)
setCurrentSpecies(david, 1)

getFunctionalAnnotationChartFile(david, threshold=1, "g1vRev.DEGS.58.DAVID.txt")
```

*Rerun G1rev with default background, negative fold change genes and 1FC cut-off*

```{r}
g1vrev <- read.xlsx("../shared_data/G1vRev_data.xlsx", colNames=TRUE, rowNames=TRUE)
g1vrev <- tibble::rownames_to_column(g1vrev,"Gene")

g1vrev.neg.degs <- g1vrev %>% filter(adp <= 0.05 & logFC <= -1)
#g1vrev.bkground <- g1vrev %>% dplyr::select(c("Gene"))

g1vrev.neg.degs.ensID <- na.omit(mapIds(org.Hs.eg.db, keys = g1vrev.neg.degs$Gene, keytype = "SYMBOL", column="ENSEMBL"))
#g1vrev.bkground.ensID <- na.omit(mapIds(org.Hs.eg.db, keys = g1vrev.bkground$Gene, keytype = "SYMBOL", column="ENSEMBL"))

david<-DAVIDWebService$new(email="charliew@mit.edu", url="https://david.ncifcrf.gov/webservice/services/DAVIDWebService")

result<-addList(david, g1vrev.neg.degs.ensID, idType="ENSEMBL_GENE_ID", 
                listName="g1vrev.neg.degs", listType="Gene")

#result<-addList(david, g1vrev.bkground.ensID, idType="ENSEMBL_GENE_ID", 
#                listName="g1vrev.bkground", listType="Background")

setAnnotationCategories(david, c("GOTERM_BP_DIRECT","GOTERM_MF_DIRECT", "GOTERM_CC_DIRECT", 
                                 "KEGG_PATHWAY", "REACTOME_PATHWAY","BIOCARTA"))

setCurrentGeneListPosition(david, 1)
setCurrentBackgroundPosition(david, 1)
setCurrentSpecies(david, 1)

getFunctionalAnnotationChartFile(david, threshold=1, "g1vRev.revDEGS.1.DAVID.txt")
```

*Rerun G1rev with default background, negative fold change genes and a relaxed cut-off*

```{r}
g1vrev <- read.xlsx("../shared_data/G1vRev_data.xlsx", colNames=TRUE, rowNames=TRUE)
g1vrev <- tibble::rownames_to_column(g1vrev,"Gene")

g1vrev.neg.degs <- g1vrev %>% filter(adp <= 0.05 & logFC <= -0.58)
#g1vrev.bkground <- g1vrev %>% dplyr::select(c("Gene"))

g1vrev.neg.degs.ensID <- na.omit(mapIds(org.Hs.eg.db, keys = g1vrev.neg.degs$Gene, keytype = "SYMBOL", column="ENSEMBL"))
#g1vrev.bkground.ensID <- na.omit(mapIds(org.Hs.eg.db, keys = g1vrev.bkground$Gene, keytype = "SYMBOL", column="ENSEMBL"))

david<-DAVIDWebService$new(email="charliew@mit.edu", url="https://david.ncifcrf.gov/webservice/services/DAVIDWebService")

result<-addList(david, g1vrev.neg.degs.ensID, idType="ENSEMBL_GENE_ID", 
                listName="g1vrev.neg.degs", listType="Gene")

#result<-addList(david, g1vrev.bkground.ensID, idType="ENSEMBL_GENE_ID", 
#                listName="g1vrev.bkground", listType="Background")

setAnnotationCategories(david, c("GOTERM_BP_DIRECT","GOTERM_MF_DIRECT", "GOTERM_CC_DIRECT", 
                                 "KEGG_PATHWAY", "REACTOME_PATHWAY","BIOCARTA"))

setCurrentGeneListPosition(david, 1)
setCurrentBackgroundPosition(david, 1)
setCurrentSpecies(david, 1)

getFunctionalAnnotationChartFile(david, threshold=1, "g1vRev.revDEGS.58.DAVID.txt")
```

## write session info*

```{r}
sessionInfo()
writeLines(capture.output(sessionInfo()), "sessionInfo.txt")
```